### 2020-10-30 outputs/paper/paper.Rmd

---
title: "TBD"
subtitle: "TBD"
author: "TBD"
thanks: "Code and data are available at: LINK."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: |
  | First sentence. Second sentence. Third sentence. Fourth sentence. 
output:
  bookdown::pdf_document2:
toc: FALSE
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(palmerpenguins)
```

# Introduction

Here's a dumb example of how to use some references: In paper we run our analysis in `R` [@citeR]. We also use the `tidyverse` which was written by @thereferencecanbewhatever If we were interested in baseball data then @citeLahman could be useful.

# Data

Our data is of penguins (Figure \@ref(fig:bills)).

```{r bills, fig.cap="Bills of penguins", echo = FALSE}
ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = FALSE) +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk more about it.

Also bills and their average (Figure \@ref(fig:billssssss)). (Notice how you can change the height and width so they don't take the whole page?)

```{r billssssss, fig.cap="More bills of penguins", echo = FALSE, fig.width=8, fig.height=4}

# This needs to be about the random data tha tI sasmpled?
ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = FALSE) +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk way more about it.

# Model

The model we use to predict the result of the election is MRP, multilevel regression with post-stratification. Logistic regression allows us the simplicity of analyzing the categorical response variable while incorporating both numerical and categorical explanatory variables; while combined with post-stratification it yields a prediction result closer to the population parameter.

We are interested in how variables such as age, education, race, family income, and geographic region affect citizens’ voting intentions. The response variable that we are interested in is the chances of a citizen voting for Trump in the coming presidential election. It is a categorical variable with two levels: 1 represents intending to vote for Donald Trump, and 2 means planning to vote for Joe Biden.

First, we train a multilevel logistic regression model using raw data from DATA towards the variable of interest using our x explanatory variables. We then apply this model to our post-stratification data set to get the estimates.

Logistic regression estimates $\beta_0...\beta_k$ in equation \@ref(eq:logistic)

\begin{equation}
log(\frac{p}{1-p})=\beta_0+\beta_1x_1+...+\beta_kx_k (\#eq:logistic)
\end{equation}

where p is the probability of event A that we are interested in, $\beta_0$is the intercept, $x_1...x_K$ are our variables of interest and $\beta_1...\beta_k$ are parameters for each of these variables. Based on the result, we are able to estimate p for a particular case given all the variables.

In our case, we want to estimate $\beta_{age},\beta_{education},\beta_{race},\beta_{income},\beta_{state}$ in \@ref(eq:logvar).

\begin{equation}
log(\frac{p}{1-p})=\beta_0+\beta_{age}x_{age}
+\beta_{education}x_{education}+\beta_{race}x_{race}
+\beta_{income}x_{income}+\beta_{state}x_{state}(\#eq:logvar)
\end{equation}

where p is the probability that the respondent votes for Trump, $\beta_0$ is the intercept, $\beta_{age}$ is the parameter for age, $\beta_{education}$ is the parameter for education level, $\beta_{race}$ is the parameter for race, $\beta_{income}$ is the parameter for income, and $\beta_{state}$ is the parameter for the state the respondent is in.

The logic behind post-stratification is that we divide the sample data into strata based on a few attributes such as state, income, education level. Then we come up with a weight for each stratum to adjust its influence towards our prediction. Namely, if a stratum is over-represented, we want to reduce its impact on the result; if a stratum is under-represented, we want to increase its influence.
We need a post-stratification dataset that is large enough to do this. In this report, we use the ACS(reason).

The post-stratification estimate is defined by $\hat{y}_{PS} = \frac{\sum{N_j\hat{y}_j}}{\sum{N_j}}$ where $\hat{y}_j$ is the estimate of y in cell j, and $N_j$ is the size of the j-th cell in the population.

Notably, the multilevel regression before post-stratification produces a proportion for the post-stratification based on regression, instead of merely averaging the sample in each stratum.

We fit two nested multilevel logistic regressions for estimating candidate support in each cell.

*Formula of the first model

That is the probability that a respondent has the intention to vote for either Trump or Biden.

And the second model predicts:

**Formula of the second model

That is the probability that a respondent has the intention to vote for Trump, given that he/she either has the intention to vote for Trump or Biden.

Together, mod1 and mod2 form a Bayesian model to predict whether Donald Trump will win the election.

# Results

# Discussion

## First discussion point

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

# Appendix {-}

\newpage

# References

### 2020-10-31 scripts/01-data-cleaning-survey.R
binary variable

@@ -1,0 +1,61 @@
+#### Preamble ####
+# Purpose: Prepare and clean the survey data downloaded from [...UPDATE ME!!!!!]
+# Author: Arjun Dhatt, Ben Draskovic, Gantavya Gupta, Yiqu Ding 
+# Data: 2 October 2020
+# Contact: arjun.dhatt@mail.utoronto.ca 
+# License: MIT
+# Pre-requisites: 
+# - Need to have downloaded the data from X and save the folder that you're 
+# interested in to inputs/data 
+# - Don't forget to gitignore it!
+
+
+
+#### Workspace setup ####
+library(haven)
+library(tidyverse)
+# Read in the raw data (You might need to change this if you use a different dataset)
+raw_data <- read_dta("inputs/ns20200625/ns20200625.dta")
+# Add the labels
+raw_data <- labelled::to_factor(raw_data)
+# Just keep some variables
+reduced_data <- 
+  raw_data %>% 
+  select(interest,
+         registration,
+         vote_2016,
+         vote_intention,
+         vote_2020,
+         ideo5,
+         employment,
+         foreign_born,
+         gender,
+         census_region,
+         hispanic,
+         race_ethnicity,
+         household_income,
+         education,
+         state,
+         congress_district,
+         age) 
+
+ps3_data <- 
+  raw_data %>% 
+  select(age,
+         education, hispanic,household_income, race_ethnicity,extra_covid_worn_mask,state, trump_biden
+         ) %>% 
+ mutate(binary = case_when(
+   trump_biden == "Donald Trump" ~ 1,
+   trump_biden == "Joe Biden" ~ 2
+ )) %>% 
+  filter(!is.na(binary))
+
+write_csv(ps3_data, "outputs/clean-survey.csv")
+
+#### What else???? ####
+# Maybe make some age-groups?
+# Maybe check the values?
+# The vote is not a binary variable, it contains 758 "Don't Know", 2626 "Donald Trump", 3075 "Joe Biden" and 20 NAs. 
+# We resolved this by deleting the "Don't know" and NA responses, since it was a relatively small (12%) part of our
+# data set.
+

### 2020-10-31 scripts/01-data-cleaning-survey.R
2.11

@@ -33,6 +33,7 @@ tbdata <-
 
 write_csv(ps3_data, "outputs/clean-survey.csv")
 
+
 #### What else???? ####
 # Maybe make some age-groups?
 # Maybe check the values?

### 2020-10-31 scripts/01-data-cleaning-survey.R
Update 01-data-cleaning-survey.R

@@ -36,12 +36,10 @@ write_csv(ps3_data, "outputs/clean-survey.csv")
 #### What else???? ####
 # Maybe make some age-groups?
 # Maybe check the values?
-<<<<<<< HEAD:outputs/Data Cleaning.csv
 # Is vote a binary? If not, what are you going to do?
 
-=======
+
 # The vote is not a binary variable, it contains 758 "Don't Know", 2626 "Donald Trump", 3075 "Joe Biden" and 20 NAs. 
 # We resolved this by deleting the "Don't know" and NA responses, since it was a relatively small (12%) part of our
 # data set.
->>>>>>> 601c4189ad0cf63aacc0d2a1df8faaeab0aceeb9:scripts/01-data-cleaning-survey.R
 

### 2020-10-31 scripts/01-data-cleaning-survey.R
3.44

@@ -1,25 +1,26 @@
 #### Preamble ####
-# Purpose: Prepare and clean the survey data downloaded from [...UPDATE ME!!!!!]
+# Purpose: The purpose of this code is to prepare and clean the Nationscape Data Set downloaded from the Democracy Fund Voter Study Group. Because we aren't looking at each and every one of the more than 200 variables included in the dataset, we want to clean the dataset so that it only includes variables that we are interested in. To address this issue, we only included the variables that we are interested in. Also, in our analysis, we will only be looking at who is going to win the popular vote between Donald Trump and Joe Biden, therefore we cleaned the results so that they only showcase those who are willing to vote for Donald Trump or Joe Biden.
 # Author: Arjun Dhatt, Ben Draskovic, Gantavya Gupta, Yiqu Ding 
-# Data: 2 October 2020
+# Data: 2 November 2020
 # Contact: arjun.dhatt@mail.utoronto.ca 
 # License: MIT
 # Pre-requisites: 
-# - Need to have downloaded the data from X and save the folder that you're 
-# interested in to inputs/data 
-# - Don't forget to gitignore it!
-
-
+ ## 1. Go to: https://www.voterstudygroup.org/publication/nationscape-data-set
+ ## 2. Look for the ‘Download the Full Data Set’ heading and enter your information and submit your request. After a short period of time, you will have received an email containing links to the dataset. 
+ ## 3. Click on the link included in the email. Under the header ‘Download Resources’, download the .dta. files. This will be a zip file, therefore you will have to unzip it.
+ ## 4. After unzipping the file, open ‘phase_2_v20200814’ -> ‘ns20200625’ -> ’01-data_cleaning-survey.R’. We open the folder pertaining to ‘ns20200625’ because we want data from June 25th, 2020. 
+ ## 5. We want to then open ’01-data_cleaning-survey.R’ in R that way we can filter the dataset to our needs. 
+ ## 6. You may need to adjust the file paths depending on your system. 
 
 #### Workspace setup ####
 library(haven)
 library(tidyverse)
-# Read in the raw data (You might need to change this if you use a different dataset)
+# Read in the raw data 
 raw_data <- read_dta("inputs/ns20200625/ns20200625.dta")
-# Add the labels
+# Add labels
 raw_data <- labelled::to_factor(raw_data)
[…]

### 2020-10-31 scripts/data-cleaning-survey.R
Final COmmit

@@ -1,0 +1,48 @@
+#### Preamble ####
+# Purpose: The purpose of this code is to prepare and clean the Nationscape Data Set downloaded from the Democracy Fund Voter Study Group. Because we aren't looking at each and every one of the more than 200 variables included in the dataset, we want to clean the dataset so that it only includes variables that we are interested in. To address this issue, we only included the variables that we are interested in. Also, in our analysis, we will only be looking at who is going to win the popular vote between Donald Trump and Joe Biden, therefore we cleaned the results so that they only showcase those who are willing to vote for Donald Trump or Joe Biden.
+# Author: Arjun Dhatt, Ben Draskovic, Gantavya Gupta, Yiqu Ding 
+# Data: 2 November 2020
+# Contact: arjun.dhatt@mail.utoronto.ca 
+# License: MIT
+# Pre-requisites: 
+ ## 1. Go to: https://www.voterstudygroup.org/publication/nationscape-data-set
+ ## 2. Look for the ‘Download the Full Data Set’ heading and enter your information and submit your request. After a short period of time, you will have received an email containing links to the dataset. 
+ ## 3. Click on the link included in the email. Under the header ‘Download Resources’, download the .dta. files. This will be a zip file, therefore you will have to unzip it.
+ ## 4. After unzipping the file, open ‘phase_2_v20200814’ -> ‘ns20200625’ -> ’01-data_cleaning-survey.R’. We open the folder pertaining to ‘ns20200625’ because we want data from June 25th, 2020. 
+ ## 5. We want to then open ’01-data_cleaning-survey.R’ in R that way we can filter the dataset to our needs. 
+ ## 6. You may need to adjust the file paths depending on your system. 
+
+
+#### Workspace setup ####
+library(haven)
+library(tidyverse)
+# Read in the raw data 
+raw_data <- read_dta("inputs/ns20200625/ns20200625.dta")
+# Add labels
+raw_data <- labelled::to_factor(raw_data)
+
+# Keeping important variables
+tbdata <- 
+  raw_data %>% 
+  select(age,
+         education, hispanic,household_income, race_ethnicity,extra_covid_worn_mask,state, trump_biden
+         ) %>% 
+ mutate(binary = case_when(
+   trump_biden == "Donald Trump" ~ 1,
+   trump_biden == "Joe Biden" ~ 2
+ )) %>% 
+  filter(!is.na(binary))
+
[…]

### 2020-10-31 scripts/01-data-cleaning-survey.R
X

@@ -12,6 +12,7 @@
  ## 5. We want to then open ’01-data_cleaning-survey.R’ in R that way we can filter the dataset to our needs. 
  ## 6. You may need to adjust the file paths depending on your system. 
 
+
 #### Workspace setup ####
 library(haven)
 library(tidyverse)

### 2020-10-31 outputs/paper/paper.Rmd
Update paper.Rmd

@@
 knitr::opts_chunk$set(echo = TRUE)
-
 library(tidyverse)
-library(palmerpenguins)
 ```
@@
 
-Here's a dumb example of how to use some references: In paper we run our analysis in `R` [@citeR].
-We also use the `tidyverse` which was written by @thereferencecanbewhatever If we were interested in baseball data then @citeLahman could be useful.
-
 # Data
-
-Our data is of penguins (Figure \@ref(fig:bills)).
-
-```{r bills, fig.cap="Bills of penguins", echo = FALSE}
-ggplot(penguins, aes(x = island, fill = species)) +
-  geom_bar(alpha = 0.8) +
-  scale_fill_manual(values = c("darkorange","purple","cyan4"),
-                    guide = FALSE) +
-  theme_minimal() +
-  facet_wrap(~species, ncol = 1) +
-  coord_flip()
-```
-
-Talk more about it.
-
-Also bills and their average (Figure \@ref(fig:billssssss)). (Notice how you can change the height and width so they don't take the whole page?)
-
-```{r billssssss, fig.cap="More bills of penguins", echo = FALSE, fig.width=8, fig.height=4}
-
-# This needs to be about the random data tha tI sasmpled?
-ggplot(penguins, aes(x = island, fill = species)) +
-  geom_bar(alpha = 0.8) +
-  scale_fill_manual(values = c("darkorange","purple","cyan4"),
-                    guide = FALSE) +
-  theme_minimal() +
-  facet_wrap(~species, ncol = 1) +
-  coord_flip()
-```
-
-Talk way more about it.
 
@@
 
-First, we train a multilevel logistic regression model using raw data from DATA towards the variable of interest using our x explanatory variables.
+First, we train a multilevel logistic regression model using raw data obtained from the voter study group towards the variable of interest using the 7 explanatory variables.
 We then apply this model to our post-stratification data set to get the estimates.
@@
 
-In our case, we want to estimate $\beta_{age},\beta_{education},\beta_{race},\beta_{income},\beta_{state}$ in \@ref(eq:logvar).
-
-\begin{equation}
-log(\frac{p}{1-p})=\beta_0+\beta_{age}x_{age}
-+\beta_{education}x_{education}+\beta_{race}x_{race}
-+\beta_{income}x_{income}+\beta_{state}x_{state}(\#eq:logvar)
-\end{equation}
-
-where p is the probability that the respondent votes for Trump, $\beta_0$ is the intercept, $\beta_{age}$ is the parameter for age, $\beta_{education}$ is the parameter for education level, $\beta_{race}$ is the parameter for race, $\beta_{income}$ is the parameter for income, and $\beta_{state}$ is the parameter for the state the respondent is in.
-
 The logic behind post-stratification is that we divide the sample data into strata based on a few attributes such as state, income, education level.
 Then we come up with a weight for each stratum to adjust its influence towards our prediction.
-Namely, if a stratum is over-represented, we want to reduce its impact on the result; if a stratum is under-represented, we want to increase its influence.
+Namely, if a stratum is over-represented, we want to reduce its impact on the prediction result; if a stratum is under-represented, we want to increase its influence.
 We need a post-stratification dataset that is large enough to do this. In this report, we use the ACS(reason).
@@
 The post-stratification estimate is defined by $\hat{y}_{PS} = \frac{\sum{N_j\hat{y}_j}}{\sum{N_j}}$ where $\hat{y}_j$ is the estimate of y in cell j, and $N_j$ is the size of the j-th cell in the population.
+An illustration using the education variable is $\hat{y}_{edu}^{PS} = \frac{\sum_{j\in J_{edu}}{N_j\hat{y}_j}}{\sum_{j\in J_{edu}}{N_j}}$, we can get an estimation given any level of education of respondents, $J_{edu}$ denotes all subsets of education levels, $\cup_{i\in J} J^{edu}_{i} =$ all possible education levels.
 
-Notably, the multilevel regression before post-stratification produces a proportion for the post-stratification based on regression, instead of merely averaging the sample in each stratum.
+The multilevel regression before post-stratification produces a proportion for the post-stratification based on regression, instead of merely averaging the sample in each stratum.
+Specifically, all possible combinations of cells are from combining:
 
-We fit two nested multilevel logistic regressions for estimating candidate support in each cell.
+-
+-
+-
+-
+-
+-
 
-*Formula of the first model
+We fit the logistic regressions for estimating candidate support in each cell. We used `function` from `package` to fit \@ref(eq:model).
 
-That is the probability that a respondent has the intention to vote for either Trump or Biden.
+\begin{equation}
+P(Trump) = logit^{-1}(
+\beta_0 + \beta_age + \beta_{j[i]}^{edu} + \beta_{j[i]}^{race}
++ \beta_{j[i]}^{income} + \beta_{j[i]}^{state} + \beta_{j[i]}^{mask}
+) (\#eq:model)
+\end{equation}
 
-And the second model predicts:
+\@ref(eq:model) is the model that we fit using the survey data, with $\beta_{j[i]}^{var} \sim N(0, \sigma^2_{var})$. 
+$\beta_0$ is the intercept,each of $\beta_{j[i]}^{var}$ represents the parameter for the i-th respondent in j-th cell.
+For example, $\beta_{j[i]}^{state}$ can take values from $\beta$ for all states in the US.
+Then the model sums up estimates for each cell to the population.
 
-**Formula of the second model
-
-That is the probability that a respondent has the intention to vote for Trump, given that he/she either has the intention to vote for Trump or Biden.
-
-Together, mod1 and mod2 form a Bayesian model to predict whether Donald Trump will win the election.
+We find the mask parameter interesting, firstly because US is the country with the most COVID cases in the world, the influence of COVID on election choices is inevitable.
+Secondly, since Trump and Biden have very opposites towards the pandemic and how to handle it, this parameter will likely represent part of respondent's voting intention in the same way as any more common political indicators.
 
 # Results
+
+```{r}
+fit <- stan_glmer(#try using glmer()
+  binary ~ factor(male) + factor(male) * factor(age) +
+    (1 | state) + (1 | age) + (1 | eth) + (1 | income),
+  family = binomial(link = "logit"),
+  data = clean_survey#all age, state etc coming from post-strat
+)
+```
+
+```{r}
+# to get the estimated proportions and associated 95% PIs by state
+res_state <- fit %>%
+  add_predicted_draws(newdata=state_prop %>% 
+                        filter(age_group>20, age_group<80, decade_married>1969),
+                      allow_new_levels=TRUE) %>%
+  rename(kept_name_predict = .prediction) %>% 
+  mutate(kept_name_predict_prop = kept_name_predict*prop) %>% 
+  group_by(state_name, .draw) %>% 
+  summarise(kept_name_predict = sum(kept_name_predict_prop)) %>% 
+  group_by(state_name) %>% 
+  summarise(mean = mean(kept_name_predict), 
+            lower = quantile(kept_name_predict, 0.025), 
+            upper = quantile(kept_name_predict, 0.975))
+```
+
+```{r}
+# graph by state
+res_state %>% 
+  arrange(-mean) %>% 
+  left_join(d %>%
+              group_by(state_name, kept_name) %>%
+              summarise(n = n()) %>%
+              group_by(state_name) %>%
+              mutate(prop = n/sum(n)) %>%
+              filter(kept_name==1)) %>% 
+  ggplot(aes(y = mean, x = forcats::fct_inorder(state_name), color = "MRP estimate")) + 
+  geom_point() +
+  coord_flip() + 
+  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0) + 
+  ylab("proportion keeping maiden name") + 
+  xlab("state") + 
+  geom_point(aes(state_name, prop, color = "raw data")) +
+  scale_color_manual(name = "", values = c("MRP estimate" = "black", "raw data" = "red")) + 
+  theme_bw() +
+  ggtitle("Proportion of women keeping maiden name after marriage")
+
+res_state %>% 
+  mutate(statename = str_to_title(state_name)) %>% 
+  #mutate(statename = ifelse(state_name=="district of columbia", "District of Columbia", statename)) %>% 
+  ggplot(aes(fill = mean, state = statename)) + 
+  geom_statebins() +
+  scale_fill_viridis_c(name = "proportion keeping name") +
+  theme_void()
+ggsave("state_plot.png", width = 8, height = 6)
+```
 
@@
 
-Weaknesses and next steps should also be included.
+### 1: Nested Bayesian Model /,
 

### 2020-10-31 scripts/data-cleaning-survey.R
5.52

@@ -12,7 +12,6 @@
  ## 5. We want to then open ’01-data_cleaning-survey.R’ in R that way we can filter the dataset to our needs. 
  ## 6. You may need to adjust the file paths depending on your system. 
 
-
 #### Workspace setup ####
 library(haven)
 library(tidyverse)

### 2020-10-31 scripts/data-cleaning-survey.R
6.29

@@ -32,7 +32,10 @@ tbdata <-
  )) %>% 
   filter(!is.na(binary))
 
-write_csv(ps3_data, "outputs/clean-survey.csv")
+# Removing all NA values 
+tbdatax <- na.omit(tbdata)
+
+write_csv(tbdatax, "outputs/clean-survey.csv")
 
 
 #### What else???? ####

### 2020-10-31 scripts/data-cleaning-survey.R
6.32

@@ -1,5 +1,5 @@
 #### Preamble ####
-# Purpose: The purpose of this code is to prepare and clean the Nationscape Data Set downloaded from the Democracy Fund Voter Study Group. Because we aren't looking at each and every one of the more than 200 variables included in the dataset, we want to clean the dataset so that it only includes variables that we are interested in. To address this issue, we only included the variables that we are interested in. Also, in our analysis, we will only be looking at who is going to win the popular vote between Donald Trump and Joe Biden, therefore we cleaned the results so that they only showcase those who are willing to vote for Donald Trump or Joe Biden.
+# Purpose: The purpose of this code is to prepare and clean the Nationscape Data Set downloaded from the Democracy Fund Voter Study Group. Because we aren't looking at each and every one of the more than 200 variables included in the dataset, we want to clean the dataset so that it only includes variables that we are interested in. To address this issue, we only included the variables that we are interested in. Also, in our analysis, we will only be looking at who is going to win the popular vote between Donald Trump and Joe Biden, therefore we cleaned the results so that they only showcase those willing to vote for Donald Trump or Joe Biden. A problem we encountered with the raw dataset was that a lot of the values were shown as N/A; to address this issue, we also cleaned the dataset so that it removed all N/A values meaning for each row in the dataset, every column has a meaningful value.
 # Author: Arjun Dhatt, Ben Draskovic, Gantavya Gupta, Yiqu Ding 
 # Data: 2 November 2020
 # Contact: arjun.dhatt@mail.utoronto.ca 

### 2020-11-01 outputs/paper/paper.Rmd
author and thanks

@@
 subtitle: "TBD"
-author: "TBD"
-thanks: "Code and data are available at: LINK."
+author: "Arjun Dhatt, Benjamin Draskovic, Yiqu Ding, Gantavya Gupta"
+thanks: "Code and data are available at: https://github.com/STA304-PS4/Trump-vs-Biden."
 date: "`r format(Sys.time(), '%d %B %Y')`"
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(echo = FALSE)
 library(tidyverse)
@@
 
-```{r}
+```{r, eval=FALSE}
 fit <- stan_glmer(#try using glmer()
@@
 
-```{r}
+```{r, eval=FALSE}
 # to get the estimated proportions and associated 95% PIs by state
@@
 
-```{r}
+```{r, eval=FALSE}
 # graph by state

### 2020-11-01 scripts/data-cleaning-survey.R
8.35

@@ -33,9 +33,9 @@ tbdata <-
   filter(!is.na(binary))
 
 # Removing all NA values 
-tbdatax <- na.omit(tbdata)
+tbdata <- na.omit(tbdata)
 
-write_csv(tbdatax, "outputs/clean-survey.csv")
+write_csv(tbdata, "outputs/clean-survey.csv")
 
 
 #### What else???? ####

### 2020-11-01 outputs/paper/paper.Rmd
model update

@@
 The model we use to predict the result of the election is MRP, multilevel regression with post-stratification.
-Logistic regression allows us the simplicity of analyzing the categorical response variable while incorporating both numerical and categorical explanatory variables; while combined with post-stratification it yields a prediction result closer to the population parameter.
+The advantage of this model is that it has better performance when estimating behaviors of a particular subgroup of the population.
+One can interpret MRP as a combination of multilevel logistic regression and post-stratification.
+Logistic regression allows us the simplicity of analyzing the categorical response variable while incorporating both numerical and categorical explanatory variables; while combined with post-stratification it yields a much narrower confidence interval for the estimation.
 
-We are interested in how variables such as age, education, race, family income, and geographic region affect citizens’ voting intentions.
+We are interested in how variables such as age, education, race, family income, geographic region and mask wearing decision affect citizens’ voting intentions, particular between the major party candidates, Donald Trump for the Republicans and Joe Biden for the Democratic Party.
 The response variable that we are interested in is the chances of a citizen voting for Trump in the coming presidential election.
 It is a categorical variable with two levels: 1 represents intending to vote for Donald Trump, and 2 means planning to vote for Joe Biden.
+
+Ideally, we ought to run a pre-analysis to determine the variables of interest.
+However due to the limited time and budget, we will leave that open for further analysis and for future elections.
+We chose the explanatory variables based on our understanding of the major characteristics of a respondent that could potentially affect a his/hers voting intention.
+Except for respondents' age, education, income level and state which are common in statistical studies, we are very interested in respondent's habits towards mask-wearing, firstly because US is the country with the most COVID cases in the world, the influence of COVID on the election votes is inevitable.
+Secondly, since Trump and Biden hold quite opposites opinions towards the handling of the pandemic, this parameter will likely represent part of respondent's voting intention in the same way as the more common political indicators.
 
@@
 Based on the result, we are able to estimate p for a particular case given all the variables.
+We use `as.factors()` to incorporate dummy variables for all the categorical variable.
 
-The logic behind post-stratification is that we divide the sample data into strata based on a few attributes such as state, income, education level.
+The main logic behind post-stratification is that we divide the sample data into strata based on a few attributes such as state, income, education level.
 Then we come up with a weight for each stratum to adjust its influence towards our prediction.
 Namely, if a stratum is over-represented, we want to reduce its impact on the prediction result; if a stratum is under-represented, we want to increase its influence.
-We need a post-stratification dataset that is large enough to do this. In this report, we use the ACS(reason).
+In this sense, the combination with logistic regression allows subgroups with a relatively low size to 'reference' from other subgroups with similar characteristics.
+
+To mimic the population as closely as possible, we need a post-stratification dataset that is large enough to reference to. In this report, we use the ACS(reason).
 
@@
 Then the model sums up estimates for each cell to the population.
-
-We find the mask parameter interesting, firstly because US is the country with the most COVID cases in the world, the influence of COVID on election choices is inevitable.
-Secondly, since Trump and Biden have very opposites towards the pandemic and how to handle it, this parameter will likely represent part of respondent's voting intention in the same way as any more common political indicators.
 

### 2020-11-01 scripts/01-data-cleaning-survey.R
scripts updated

@@ -33,7 +33,9 @@ tbdata <-
  )) %>% 
   filter(!is.na(binary))
 
-write_csv(ps3_data, "outputs/clean-survey.csv")
+tbdata <- na.omit(tbdata)
+
+write_csv(tbdata, "outputs/clean-survey.csv")
 
 
 #### What else???? ####

### 2020-11-01 scripts/data-cleaning-survey.R

@@ -1,50 +1,0 @@
-#### Preamble ####
-# Purpose: The purpose of this code is to prepare and clean the Nationscape Data Set downloaded from the Democracy Fund Voter Study Group. Because we aren't looking at each and every one of the more than 200 variables included in the dataset, we want to clean the dataset so that it only includes variables that we are interested in. To address this issue, we only included the variables that we are interested in. Also, in our analysis, we will only be looking at who is going to win the popular vote between Donald Trump and Joe Biden, therefore we cleaned the results so that they only showcase those willing to vote for Donald Trump or Joe Biden. A problem we encountered with the raw dataset was that a lot of the values were shown as N/A; to address this issue, we also cleaned the dataset so that it removed all N/A values meaning for each row in the dataset, every column has a meaningful value.
-# Author: Arjun Dhatt, Ben Draskovic, Gantavya Gupta, Yiqu Ding 
-# Data: 2 November 2020
-# Contact: arjun.dhatt@mail.utoronto.ca 
-# License: MIT
-# Pre-requisites: 
- ## 1. Go to: https://www.voterstudygroup.org/publication/nationscape-data-set
- ## 2. Look for the ‘Download the Full Data Set’ heading and enter your information and submit your request. After a short period of time, you will have received an email containing links to the dataset. 
- ## 3. Click on the link included in the email. Under the header ‘Download Resources’, download the .dta. files. This will be a zip file, therefore you will have to unzip it.
- ## 4. After unzipping the file, open ‘phase_2_v20200814’ -> ‘ns20200625’ -> ’01-data_cleaning-survey.R’. We open the folder pertaining to ‘ns20200625’ because we want data from June 25th, 2020. 
- ## 5. We want to then open ’01-data_cleaning-survey.R’ in R that way we can filter the dataset to our needs. 
- ## 6. You may need to adjust the file paths depending on your system. 
-
-#### Workspace setup ####
-library(haven)
-library(tidyverse)
-# Read in the raw data 
-raw_data <- read_dta("inputs/ns20200625/ns20200625.dta")
-# Add labels
-raw_data <- labelled::to_factor(raw_data)
-
-# Keeping important variables
-tbdata <- 
-  raw_data %>% 
-  select(age,
-         education, hispanic,household_income, race_ethnicity,extra_covid_worn_mask,state, trump_biden
[…]

### 2020-11-01 scripts/01-data-cleaning-survey.R
BRMS FIRST

@@ -29,7 +29,7 @@ tbdata <-
          ) %>% 
  mutate(binary = case_when(
    trump_biden == "Donald Trump" ~ 1,
-   trump_biden == "Joe Biden" ~ 2
+   trump_biden == "Joe Biden" ~ 0
  )) %>% 
   filter(!is.na(binary))
 

### 2020-11-01 scripts/01-data-cleaning-survey.R
Added Race groupings

@@ -1,14 +1,23 @@
 #### Preamble ####
-# Purpose: The purpose of this code is to prepare and clean the Nationscape Data Set downloaded from the Democracy Fund Voter Study Group. Because we aren't looking at each and every one of the more than 200 variables included in the dataset, we want to clean the dataset so that it only includes variables that we are interested in. To address this issue, we only included the variables that we are interested in. Also, in our analysis, we will only be looking at who is going to win the popular vote between Donald Trump and Joe Biden, therefore we cleaned the results so that they only showcase those who are willing to vote for Donald Trump or Joe Biden.
+# Purpose: The purpose of this code is to prepare and clean the Nationscape Data Set downloaded from 
+# the Democracy Fund Voter Study Group. Because we aren't looking at each and every one of the more than 
+# 200 variables included in the dataset, we want to clean the dataset so that it only includes variables 
+# that we are interested in. To address this issue, we only included the variables that we are interested 
+# in. Also, in our analysis, we will only be looking at who is going to win the popular vote between 
+# Donald Trump and Joe Biden, therefore we cleaned the results so that they only showcase those who are 
+# willing to vote for Donald Trump or Joe Biden.
 # Author: Arjun Dhatt, Ben Draskovic, Gantavya Gupta, Yiqu Ding 
 # Data: 2 November 2020
 # Contact: arjun.dhatt@mail.utoronto.ca 
 # License: MIT
 # Pre-requisites: 
  ## 1. Go to: https://www.voterstudygroup.org/publication/nationscape-data-set
- ## 2. Look for the ‘Download the Full Data Set’ heading and enter your information and submit your request. After a short period of time, you will have received an email containing links to the dataset. 
- ## 3. Click on the link included in the email. Under the header ‘Download Resources’, download the .dta. files. This will be a zip file, therefore you will have to unzip it.
- ## 4. After unzipping the file, open ‘phase_2_v20200814’ -> ‘ns20200625’ -> ’01-data_cleaning-survey.R’. We open the folder pertaining to ‘ns20200625’ because we want data from June 25th, 2020. 
[…]

### 2020-11-01 scripts/data-cleaning-survey.R
1.49

@@ -1,6 +1,5 @@
 #### Preamble ####
-# Purpose: The purpose of this code is to prepare and clean the Nationscape Data Set downloaded from the Democracy Fund Voter Study Group. Because we aren't looking at each and every one of the more than 200 variables included in the dataset, we want to clean the dataset so that it only includes variables that we are interested in. To address this issue, we only included the variables that we are interested in. Also, in our analysis, we will only be looking at who is going to win the popular vote between Donald Trump and Joe Biden, therefore we cleaned the results so that they only showcase those willing to vote for Donald Trump or Joe Biden. A problem we encountered with the raw dataset was that a lot of the values were shown as N/A; to address this issue, we also cleaned the dataset so that it removed all N/A values meaning for each row in the dataset, every column has a meaningful value.
-# Author: Arjun Dhatt, Ben Draskovic, Gantavya Gupta, Yiqu Ding 
+# Purpose: The purpose of this code is to prepare and clean the Nationscape Data Set downloaded from the Democracy Fund Voter Study Group. Because we aren't looking at each and every one of the more than 200 variables included in the dataset, we want to clean the dataset so that it only includes variables that we are interested in. To address this issue, we only included the variables that we are interested in. Also, in our analysis, we will only be looking at who is going to win the popular vote between Donald Trump and Joe Biden, therefore we cleaned the results so that they only showcase those willing to vote for Donald Trump or Joe Biden. We also added another variable that was not originally included in the dataset to make vote a binary variable. A problem we encountered with the raw dataset was that a lot of the values were shown as N/A; to address this issue, we also cleaned the dataset so that it removed all N/A values meaning for each row in the dataset, every column has a meaningful value.# Author: Arjun Dhatt, Ben Draskovic, Gantavya Gupta, Yiqu Ding 
 # Data: 2 November 2020
 # Contact: arjun.dhatt@mail.utoronto.ca 
 # License: MIT
@@ -15,12 +14,14 @@
 #### Workspace setup ####
 library(haven)
 library(tidyverse)
+
 # Read in the raw data 
 raw_data <- read_dta("inputs/ns20200625/ns20200625.dta")
+
 # Add labels
 raw_data <- labelled::to_factor(raw_data)
 
-# Keeping important variables
[…]

### 2020-11-01 outputs/paper/paper.Rmd
scripts updated

--- 2020-11-01 outputs/paper/paper.Rmd
@@
 The model we use to predict the result of the election is MRP, multilevel regression with post-stratification.
-Logistic regression allows us the simplicity of analyzing the categorical response variable while incorporating both numerical and categorical explanatory variables; while combined with post-stratification it yields a prediction result closer to the population parameter.
+The advantage of this model is that it has better performance when estimating behaviors of a particular subgroup of the population.
+One can interpret MRP as a combination of multilevel logistic regression and post-stratification.
+Logistic regression allows us the simplicity of analyzing the categorical response variable while incorporating both numerical and categorical explanatory variables; while combined with post-stratification, it yields a much narrower confidence interval for the estimation.
 
-We are interested in how variables such as age, education, race, family income, and geographic region affect citizens’ voting intentions.
+We are interested in how variables such as age, education, race, family income, geographic region, and mask-wearing decision affect citizens’ voting intentions, particularly between the major party candidates, Donald Trump for the Republicans and Joe Biden for the Democratic Party.
 The response variable that we are interested in is the chances of a citizen voting for Trump in the coming presidential election.
@@
 
-First, we train a multilevel logistic regression model using raw data obtained from the voter study group towards the variable of interest using the 7 explanatory variables.
+Ideally, we ought to run a pre-analysis to determine the variables of interest.
+However, we will leave that open for further analysis and future elections due to the limited time and budget.
+We chose the explanatory variables based on our understanding of a respondent’s significant characteristics that could potentially affect his/her voting intention.
+Except for respondents' age, education, income level, and state(common in statistical studies), we are very interested in the respondent's habits towards mask-wearing.
+Firstly because the US is the country with the most COVID cases globally, the influence of COVID on the electoral votes is inevitable.
+Secondly, since Trump and Biden hold quite opposites opinions towards handling the pandemic, this parameter will likely represent part of the respondent's voting intention in the same way as the more familiar political indicators.
+
+First, we train a multilevel logistic regression model using raw data from the voter study group towards the variable of interest using the seven explanatory variables.
 We then apply this model to our post-stratification data set to get the estimates.
 
-Logistic regression estimates $\beta_0...\beta_k$ in equation \@ref(eq:logistic)
+Logistic regression estimates $\beta_0...\beta_k$ in  \@ref(eq:logistic)
 
@@
 Based on the result, we are able to estimate p for a particular case given all the variables.
+We use `as.factors()` to incorporate dummy variables for all the categorical variable.
 
-The logic behind post-stratification is that we divide the sample data into strata based on a few attributes such as state, income, education level.
+The main logic behind post-stratification is that we divide the sample data into strata based on a few attributes such as state, income, education level.
 Then we come up with a weight for each stratum to adjust its influence towards our prediction.
 Namely, if a stratum is over-represented, we want to reduce its impact on the prediction result; if a stratum is under-represented, we want to increase its influence.
-We need a post-stratification dataset that is large enough to do this. In this report, we use the ACS(reason).
+In this sense, the combination with logistic regression allows subgroups with a relatively small size to 'reference' from other subgroups with similar characteristics.
+
+To mimic the population as closely as possible, we need a post-stratification dataset large enough to refer to. In this report, we use the ACS(reason).
 
@@
 
-The multilevel regression before post-stratification produces a proportion for the post-stratification based on regression, instead of merely averaging the sample in each stratum.
-Specifically, all possible combinations of cells are from combining:
+\@ref(eq:logistic) produces a proportion for the post-stratification based on regression, instead of merely averaging the sample in each stratum.
+Specifically, all possible cells are determined from combining:
 
--
--
--
--
--
--
+- 76 different ages;
+- 11 education levels
+- 15 races;
+- 24 income levels;
+- 51 states
+- 2 options for mask wearing habits.
+
+That is
 
@@
 
-We find the mask parameter interesting, firstly because US is the country with the most COVID cases in the world, the influence of COVID on election choices is inevitable.
-Secondly, since Trump and Biden have very opposites towards the pandemic and how to handle it, this parameter will likely represent part of respondent's voting intention in the same way as any more common political indicators.
-
 # Results
 
-```{r, eval=FALSE}
-fit <- stan_glmer(#try using glmer()
-  binary ~ factor(male) + factor(male) * factor(age) +
-    (1 | state) + (1 | age) + (1 | eth) + (1 | income),
-  family = binomial(link = "logit"),
-  data = clean_survey#all age, state etc coming from post-strat
+```{r, eval = FALSE}
+fit <- brms::brm(
+  binary ~ (1 | state) + (1 | age) + (1 | education) + (1 | household_income),
+  family = bernoulli(link = "logit"),
+  data = clean_survey
 )
+print(fit)
 ```
@@
 
-### 1: Nested Bayesian Model /,
+### 1: Nested Bayesian Model
+
+### 2: Pre-analysis
 

### 2020-11-01 scripts/01-data-cleaning-survey.R
1.58

@@ -1,11 +1,13 @@
 #### Preamble ####
-# Purpose: The purpose of this code is to prepare and clean the Nationscape Data Set downloaded from 
-# the Democracy Fund Voter Study Group. Because we aren't looking at each and every one of the more than 
-# 200 variables included in the dataset, we want to clean the dataset so that it only includes variables 
-# that we are interested in. To address this issue, we only included the variables that we are interested 
-# in. Also, in our analysis, we will only be looking at who is going to win the popular vote between 
-# Donald Trump and Joe Biden, therefore we cleaned the results so that they only showcase those who are 
-# willing to vote for Donald Trump or Joe Biden.
+# Purpose: The purpose of this code is to prepare and clean the Nationscape Data Set downloaded from the Democracy Fund 
+# Voter Study Group. Because we aren't looking at each and every one of the more than 200 variables included in the dataset,
+# we want to clean the dataset so that it only includes variables that we are interested in. To address this issue, we only
+# included the variables that we are interested in. Also, in our analysis, we will only be looking at who is going to win 
+# the popular vote between Donald Trump and Joe Biden, therefore we cleaned the results so that they only showcase those 
+# willing to vote for Donald Trump or Joe Biden. We also added another variable that was not originally included in the
+# dataset to make vote a binary variable. A problem we encountered with the raw dataset was that a lot of the values were 
+# shown as N/A; to address this issue, we also cleaned the dataset so that it removed all N/A values meaning for each row 
+# in the dataset, every column has a meaningful value.
 # Author: Arjun Dhatt, Ben Draskovic, Gantavya Gupta, Yiqu Ding 
 # Data: 2 November 2020
 # Contact: arjun.dhatt@mail.utoronto.ca 
@@ -26,12 +28,16 @@
 library(haven)
 library(tidyverse)
 library(dplyr)
+
 # Read in the raw data 
 raw_data <- read_dta("inputs/ns20200625/ns20200625.dta")
+
 # Add labels
 raw_data <- labelled::to_factor(raw_data)
 
 # Keeping important variables
+# Adding an extra variable that outputs a 1 if someone chooses to vote for Donald Trump in the 2020 elections 
+# and 0 otherwise
 tbdata <- 
   raw_data %>% 
   select(age,
@@ -43,6 +49,10 @@ tbdata <-
  )) %>% 
   filter(!is.na(binary))
 
[…]

### 2020-11-01 scripts/01-data-cleaning-survey.R
Update 01-data-cleaning-survey.R

@@ -14,13 +14,13 @@
 # License: MIT
 # Pre-requisites: 
  ## 1. Go to: https://www.voterstudygroup.org/publication/nationscape-data-set
- ## 2. Look for the ‘Download the Full Data Set’ heading and enter your information and submit your request. 
+ ## 2. Look for the 'Download the Full Data Set' heading and enter your information and submit your request. 
  ## After a short period of time, you will have received an email containing links to the dataset. 
- ## 3. Click on the link included in the email. Under the header ‘Download Resources’, download the .dta. 
+ ## 3. Click on the link included in the email. Under the header 'Download Resources', download the .dta. 
  ## files. This will be a zip file, therefore you will have to unzip it.
- ## 4. After unzipping the file, open ‘phase_2_v20200814’ -> ‘ns20200625’ -> ’01-data_cleaning-survey.R’. 
- ## We open the folder pertaining to ‘ns20200625’ because we want data from June 25th, 2020. 
- ## 5. We want to then open ’01-data_cleaning-survey.R’ in R that way we can filter the dataset to our needs. 
+ ## 4. After unzipping the file, open 'phase_2_v20200814' -> 'ns20200625' -> '01-data_cleaning-survey.R'. 
+ ## We open the folder pertaining to 'ns20200625' because we want data from June 25th, 2020. 
+ ## 5. We want to then open '01-data_cleaning-survey.R' in R that way we can filter the dataset to our needs. 
  ## 6. You may need to adjust the file paths depending on your system. 
 
 

### 2020-11-01 outputs/paper/paper.Rmd
5.29

@@
 # Data
+
+In this analysis, we collected data from the Nationscape dataset — a collaboration between the Democracy Fund Voter Study Group and UCLA Political Scientists.
+The Nationscape dataset that we will be analyzing was collected from June 25th, 2020 to July 1st, 2020.
+Using the data from Nationscape, we would like the predict the overall popular vote of the 2020 American presidential election using multilevel regression with post-stratification.
+
+The samples are provided by Lucid, “a market research platform that provides access to authentic, targeted audiences”.
+In order to ensure that an appropriate sample is selected, samples are selected based on a set of demographic quotas based on a multitude of factors such as age, gender, ethnicity, etc.
+Respondents of the survey are sent directly to an online survey (conducted in English) operated by the Nationscape team and forced to complete an attention check to ensure the answers they provide are meaningful.
+Lastly, the data is weighted to be representative of the American population using factors such as — gender, four major census regions, race, etc.
+
+The population in this dataset is all voting residents in the USA that are eligible to vote.
+This does not include a large population of those that reside in the US such as non-citizens or those who are incarcerated, but this is representative of a real election.
+The population frame is all voting residents in USA that have access to a computer in order to complete the online survey.
+As mentioned before, the survey is taken online, therefore it excludes those without access to a device that can take the online survey.
+The sample in this case is all respondents who complete this survey online.
+
+The data is collected using a convenience sample selected based on a set of demographic criteria.
+Because convenience sampling was used over random sampling, this can result in some biases in our dataset.
+
+The respondents of the survey are found through Lucid, which “runs an online exchange for survey respondents”.
+The respondents from the survey on Lucid are sent to the online Nationscape survey where they are prompted to complete the survey.
+Respondents who complete the survey not choose not to disclose their household income; this results in a large number of non-respondents because they may not be comfortable providing sensitive information.
+In an effort to account for the respondents who choose not to provide income, non-respondents are not weighed for income.
+
+The variables that we used in our dataset are as follow: 
+-	age
+     o	“What is your age”
+     o	It provides an integer value greater than or equal to 18
+-	education
+     o	“What is the highest level of education you have completed?” 
+     o	An extensive list of options are provided
+-	Hispanic
+     o	“Are you of Hispanic, Latino, or Spanish origin?” 
+     o	An extensive list of options are provided 
+-	household_income
+     o	“What is your current annual household income before taxes? 
+     o	Provides an extensive list of options beginning with $5,000 increments and then increases to $25,000 increments
+     o	This is the variable in our dataset that many people did not feel comfortable answering and was left as N/A.
+When        cleaning the dataset, we removed all responses that left this answer as N/A
+-	race_ethnicity
+     o	“What is your race”
+     o	An extensive list of options are provided. 
+-	extra_covid_worn_mask
+     o	“Have you done any of the following in the past week? - Worn a mask when going out in public” 
+     o	Yes or No options are available for the respondent to fill out 
+-	state
+     o	“Respondent’s state, as a two-character postal abbreviation. Calculated based on entered ZIP code.” 
+     o	Manually filled out by respondent 
+-	trump_biden
+     o	“If the general election for president of the United States was a contest between Joe Biden and Donald Trump, who        would you support? “ 
+     o	Options are either ‘Joe Biden’, ‘Donald Trump’, or ‘Don’t Know’
+
+We also created another variable called ‘binary’ which outputs the result of the variable ‘trump_biden’ as a 1 or a 0 making it binary, therefore easier to analyze.
+
+Key features of data?
+
+The dataset we used contains many strengths and weaknesses.
+One of the strengths is due to the fact that the survey is distributed online.
+In today’s age where most things are online, this ensures that we can reach a wide part of the United States.
+At the same time, this can also be viewed as a weakness because certain age groups of the United States may not be tech-savvy enough to complete an online survey.
+The older population of the united states (e.g.
+75+) may not be able to complete the survey because it is online which means that our data may not accurately reflect the older populations views regarding the 2020 election.
+A potential solution to this weakness is to use administer multiple forms of the survey to ensure that all people can access the survey.
+
+Another weakness of the data comes from the fact that we use convenience-based sampling which inherently contains bias.
+Because the sampling method is based on convenience, we may be unlucky when sampling and get a sample group that inaccurately represents the population of the US making our results meaningless.
+
+Lastly another weakness of our dataset is due to the fact that the survey data we are analyzing is collected from June 25th, 2020 to July 1st, 2020.
+Between July and November (the month of the election), many voters may not have an informed vote and their opinions may still be swayed after watching crucial debates and hearing what the leaders have to say; our data doesn’t take into consideration the people whose votes may change in the most crucial months of the election.
+A solution to this weakness can be to analyze data that may have occurred closer to the actual election so that the participants have an informed vote.
 

### 2020-11-01 outputs/paper/paper.Rmd
Update paper.Rmd

--- 2020-11-01 outputs/paper/paper.Rmd
@@
 - 24 income levels;
-- 51 states
+- 51 states;
 - 2 options for mask wearing habits.
@@
 
-```{r, eval = FALSE}
+```{r}
 fit <- brms::brm(
-  binary ~ (1 | state) + (1 | age) + (1 | education) + (1 | household_income),
+  binary ~ (1 | age) + (1 | education) + (1 | race_ethnicity0)+ (1 | hispanic)
+  + (1 | household_income) + (1 | state) + (1 | extra_covid_worn_mask),
   family = bernoulli(link = "logit"),

### 2020-11-02 scripts/01-data-cleaning-survey.R
Adding the further grouped categories

@@ -13,15 +13,15 @@
 # Contact: arjun.dhatt@mail.utoronto.ca 
 # License: MIT
 # Pre-requisites: 
- ## 1. Go to: https://www.voterstudygroup.org/publication/nationscape-data-set
- ## 2. Look for the 'Download the Full Data Set' heading and enter your information and submit your request. 
- ## After a short period of time, you will have received an email containing links to the dataset. 
- ## 3. Click on the link included in the email. Under the header 'Download Resources', download the .dta. 
- ## files. This will be a zip file, therefore you will have to unzip it.
- ## 4. After unzipping the file, open 'phase_2_v20200814' -> 'ns20200625' -> '01-data_cleaning-survey.R'. 
- ## We open the folder pertaining to 'ns20200625' because we want data from June 25th, 2020. 
- ## 5. We want to then open '01-data_cleaning-survey.R' in R that way we can filter the dataset to our needs. 
- ## 6. You may need to adjust the file paths depending on your system. 
+## 1. Go to: https://www.voterstudygroup.org/publication/nationscape-data-set
+## 2. Look for the 'Download the Full Data Set' heading and enter your information and submit your request. 
+## After a short period of time, you will have received an email containing links to the dataset. 
+## 3. Click on the link included in the email. Under the header 'Download Resources', download the .dta. 
+## files. This will be a zip file, therefore you will have to unzip it.
+## 4. After unzipping the file, open 'phase_2_v20200814' -> 'ns20200625' -> '01-data_cleaning-survey.R'. 
+## We open the folder pertaining to 'ns20200625' because we want data from June 25th, 2020. 
+## 5. We want to then open '01-data_cleaning-survey.R' in R that way we can filter the dataset to our needs. 
+## 6. You may need to adjust the file paths depending on your system. 
 
 
 #### Workspace setup ####
@@ -34,7 +34,6 @@ raw_data <- read_dta("inputs/ns20200625/ns20200625.dta")
 
 # Add labels
 raw_data <- labelled::to_factor(raw_data)
-
 # Keeping important variables
[…]

### 2020-11-02 scripts/01-data_cleaning-post-strat.R
Post Stratification Data Set

@@ -1,46 +1,154 @@
 #### Preamble ####
-# Purpose: Prepare and clean the survey data downloaded from [...UPDATE ME!!!!!]
-# Author: Rohan Alexander and Sam Caetano [CHANGE THIS TO YOUR NAME!!!!]
-# Data: 22 October 2020
-# Contact: rohan.alexander@utoronto.ca [PROBABLY CHANGE THIS ALSO!!!!]
+# Purpose: To prepare the survey data downloaded from IPUMS USA based on the 2018 ACS survey. 
+# This data set will be used in the post-stratification process. MEaning that the data will be 
+# adjusted to match the categories used in the cleaned Nation-Scape Data set. Then bin counts will
+# be generated so that the two data sets may be compared. 
+# Author: Arjun Dhatt, Ben Draskovic, Gantavya Gupta, Yiqu Ding 
+# Data: 2 November 2020
+# Contact: ben.draskovic@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: 
-# - Need to have downloaded the ACS data and saved it to inputs/data
-# - Don't forget to gitignore it!
+# - Need to have downloaded the ACS data and saved it to inputs/ACS
+# - Set up a gitignore in order to retain the privacy of the data 
 
 
 #### Workspace setup ####
 library(haven)
 library(tidyverse)
 # Read in the raw data. 
-raw_data <- read_dta("inputs/data/usa_00003.dta"
-                     )
+raw_data <- read_dta("inputs/ACS/usa_00001.dta.gz"
+)
 # Add the labels
 raw_data <- labelled::to_factor(raw_data)
 
-# Just keep some variables that may be of interest (change 
-# this depending on your interests)
+# Select variables of interest for analysis
 names(raw_data)
 
 reduced_data <- 
   raw_data %>% 
-  select(region,
-         stateicp,
-         sex, 
-         age, 
+  select(age, 
          race, 
          hispan,
-         marst, 
-         bpl,
-         citizen,
-         educd,
-         labforce,
-         inctot)
+         educ,
+         ftotinc)
 rm(raw_data)
-         
 
-#### What's next? ####
+#Remove all na values from the data (For Family income NA was 9999999)
+#Remove all children under 18
+prep_data <- reduced_data %>% 
+  filter(
+    ftotinc<9999999,
+    as.integer(age)>18,
+    !is.na(age),
[…]

### 2020-11-02 outputs/paper/paper.Rmd
packages

@@
 library(tidyverse)
+library(lme4)
+library(rstanarm)
+library(brms)
 ```
@@
 
-That is
-
-We fit the logistic regressions for estimating candidate support in each cell. We used `function` from `package` to fit \@ref(eq:model).
+That is 30,697,920 cells in total. We fit the logistic regressions for estimating candidate support in each cell. We used `function` from `package` to fit \@ref(eq:model).
 
@@
 ```{r}
-fit <- brms::brm(
-  binary ~ (1 | age) + (1 | education) + (1 | race_ethnicity0)+ (1 | hispanic)
-  + (1 | household_income) + (1 | state) + (1 | extra_covid_worn_mask),
-  family = bernoulli(link = "logit"),
-  data = clean_survey
+attach(clean_survey)
+mod <- brm(binary ~ age + education_grouped + race_ethnicity + hispanic + household_income_grouped + state + extra_covid_worn_mask,
+           data = clean_survey,
+           family = bernoulli(),
+           iter = 4000
            )
-print(fit)
+
+summary(mod)
 ```
 
-```{r, eval=FALSE}
+```{r}
+usa_00001$estimate <-
+  mod %>%
+  predict(newdata = usa_00001)
+```
+
+```{r}
 # to get the estimated proportions and associated 95% PIs by state
-res_state <- fit %>%
-  add_predicted_draws(newdata=state_prop %>% 
-                        filter(age_group>20, age_group<80, decade_married>1969),
-                      allow_new_levels=TRUE) %>%
-  rename(kept_name_predict = .prediction) %>% 
-  mutate(kept_name_predict_prop = kept_name_predict*prop) %>% 
+res_state <- mod %>%
+  tidybayes::add_predicted_draws(newdata = census_data) %>%
+  rename(president_predict = .prediction) %>%  
+  mutate(president_predict_prop = president_predict*prop) %>% 
   group_by(state_name, .draw) %>% 

### 2020-11-02 scripts/01-data_cleaning-post-strat.R
Fixed error with summarise function

@@ -15,6 +15,7 @@
 #### Workspace setup ####
 library(haven)
 library(tidyverse)
+library(dplyr)
 # Read in the raw data. 
 raw_data <- read_dta("inputs/ACS/usa_00001.dta.gz"
 )
@@ -45,7 +46,6 @@ prep_data <- reduced_data %>%
   )
 # This removes 799,716 respondants from the data 
 
-unique(prep_data$educ)
 
 #Group the education responses into groups that best match the groups in UCLA Survey being used
 #Notably an estimate as to when a degree would be completed had to be used for this we used the estimate of 3 years or above
@@ -70,20 +70,21 @@ educ0 <- recode(prep_data$educ, !!!recode_key_education)
 #Include Bi/Multi Racial individuals in other as this was not gathered in UCLA data 
 #Assuming that Bi/Multi Racial individuals would select other with no Bi/Multi Racial option
 recode_key_race <- c(  
-  "Two major races" = "Other race, nec",
-  "Three or more major races" = "Other race, nec",
-  "Chinese" = "Asian or Pacific Islander",
-  "Japanese" = "Asian or Pacific Islander",
-  "Other Asian or Pacific Islander" = "Asian or Pacific Islander"
+  "two major races" = "other race, nec",
+  "three or more major races" = "other race, nec",
+  "chinese" = "asian or pacific islander",
+  "japanese" = "asian or pacific islander",
+  "other asian or pacific islander" = "asian or pacific islander"
 )
 # After the keys is made use the recode function to create a new string based on the collumn being changed
-race0 <-recode(prep_data$race, !!!recode_key_race)
+race0 <- recode(prep_data$race, !!!recode_key_race)
 
 # Adjust the actual collumns in the data set 
 # Also group age into Age_groups and group income into Income_Groups for post-stratification, 
 prep_data <- prep_data %>% 
   mutate(
-    education_grouped = educ0
+    education_grouped = educ0,
+    race = race0
   ) %>% 
   mutate(
     age_group = case_when(
@@ -113,9 +114,8 @@ write_dta(prep_data, "outputs/post_strat_data.dta")
 #Create a new tibble that includes the count of individuals in each of our subdivided categories
 cell_counts <- prep_data %>% 
   group_by(age_group, income_group, education_grouped, race, hispan) %>% 
-  add_tally() %>% 
-  ungroup() %>% 
-  select(age_group, income_group, education_grouped, race, hispan, n)
[…]

### 2020-11-02 scripts/01-data-cleaning-survey.R
Data Super squeaky clean

@@ -56,17 +56,21 @@ tbdata <- na.omit(tbdata)
 
 #Group all of the Asian and PAcific Islander Ethnicity options in to 3 categories
 recode_key_race <- c(  
-  "Asian (Asian Indian)" = "Asian or Pacific Islander",
-  "Asian (Chinese)" = "Asian or Pacific Islander",
-  "Asian (Filipino)" = "Asian or Pacific Islander",
-  "Asian (Japanese)" = "Asian or Pacific Islander",
-  "Asian (Korean)" = "Asian or Pacific Islander",
-  "Asian (Vietnamese)" = "Asian or Pacific Islander",
-  "Asian (Other)" = "Asian or Pacific Islander",
-  "Pacific Islander (Native Hawaiian)" = "Asian or Pacific Islander",
-  "Pacific Islander (Guamanian)" = "Asian or Pacific Islander",
-  "Pacific Islander (Samoan)" = "Asian or Pacific Islander",
-  "Pacific Islander (Other)" = "Asian or Pacific Islander"
+  "Asian (Asian Indian)" = "asian or pacific islander",
+  "Asian (Chinese)" = "asian or pacific islander",
+  "Asian (Filipino)" = "asian or pacific islander",
+  "Asian (Japanese)" = "asian or pacific islander",
+  "Asian (Korean)" = "asian or pacific islander",
+  "Asian (Vietnamese)" = "asian or pacific islander",
+  "Asian (Other)" = "asian or pacific islander",
+  "Pacific Islander (Native Hawaiian)" = "asian or pacific islander",
+  "Pacific Islander (Guamanian)" = "asian or pacific islander",
+  "Pacific Islander (Samoan)" = "asian or pacific islander",
+  "Pacific Islander (Other)" = "asian or pacific islander",
+  "White" = "white",
+  "Some other race" = "other race, nec",
+  "Black, or African American" = "black/african american/negro",
+  "American Indian or Alaska Native" = "american indian or alaska native"
 )
 
 # After the key is made use the recode function to create a new string based on the collumn being changed 
@@ -106,16 +110,20 @@ household_income0 <- recode(tbdata$household_income, !!!recode_key_income)
 
 #Group the Hispanic responses into groups that match the ACS groups
 recode_key_hispanic <- c(  
-  "Argentinian" = "Other Hispanic",
[…]

### 2020-11-02 scripts/01-data_cleaning-post-strat.R

@@ -108,6 +108,7 @@ prep_data <- prep_data %>%
     age_group, income_group, education_grouped, race, hispan
   )
 
+
 # Generate the data file 
 write_dta(prep_data, "outputs/post_strat_data.dta")
 

### 2020-11-02 scripts/01-data_cleaning-post-strat.R
Changed file format to csv

@@ -119,7 +119,7 @@ cell_counts <- prep_data %>%
 
 
 #Generate the Data file of these cell counts
-write_dta(cell_counts, "outputs/post_strat_cellcount.dta")
+write_csv(cell_counts, "outputs/post_strat_cellcount.csv")
 
 #Create the proportion files needed in the modelling stage 
 #Each will be based on one of our variables of comparison 

### 2020-11-02 outputs/paper/paper.Rmd
MODEL UPDATE

@@
 attach(clean_survey)
-mod <- brm(binary ~ age + education_grouped + race_ethnicity + hispanic + household_income_grouped + state + extra_covid_worn_mask,
+mod <- brm(binary ~ age + (1|education_grouped) + race_ethnicity + hispanic + household_income_grouped + state + extra_covid_worn_mask,
            data = clean_survey,
            family = bernoulli(),
-           iter = 4000
+           iter = 4000,
+           control = list(adapt_delta = 0.98)
            )
@@
 ```{r}
-usa_00001$estimate <-
-  mod %>%
-  predict(newdata = usa_00001)
+posterior_prob <- posterior_linpred(mod, transform = TRUE, newdata = post_strat_cellcount, allow_new_levels = TRUE)
+poststrat_prob <- posterior_prob %*% post_strat_cellcount$n / sum(poststrat$n)
+model_popn_pref <- c(mean = mean(poststrat_prob), sd = sd(poststrat_prob))
+round(model_popn_pref, 3)
 ```

### 2020-11-02 scripts/01-data_cleaning-post-strat.R
Changed Collumn names to match clean-survey

@@ -84,10 +84,11 @@ race0 <- recode(prep_data$race, !!!recode_key_race)
 prep_data <- prep_data %>% 
   mutate(
     education_grouped = educ0,
-    race = race0
+    race_ethnicity = race0,
+    hispanic = hispan
   ) %>% 
   mutate(
-    age_group = case_when(
+    age = case_when(
       as.numeric(age) >=18 & as.numeric(age) <=35 ~ "18-35",
       as.numeric(age) >=36 & as.numeric(age) <=55 ~ "36-55",
       as.numeric(age) >=56 & as.numeric(age) <=75 ~ "56-75",
@@ -95,7 +96,7 @@ prep_data <- prep_data %>%
     )
   ) %>% 
   mutate(
-    income_group = case_when(
+    household_income_grouped = case_when(
       as.numeric(ftotinc) <25000 ~ "$25k or less",
       as.numeric(ftotinc) >=25000 & as.numeric(ftotinc) < 50000 ~ "$25k to $50k",
       as.numeric(ftotinc) >=50000 & as.numeric(ftotinc) < 75000 ~ "$50k to $75k",
@@ -105,7 +106,7 @@ prep_data <- prep_data %>%
     )
   ) %>% 
   select(
-    age_group, income_group, education_grouped, race, hispan
+    age, household_income_grouped, education_grouped, race_ethnicity, hispanic
   )
 
 
@@ -114,7 +115,7 @@ write_dta(prep_data, "outputs/post_strat_data.dta")
 
 #Create a new tibble that includes the count of individuals in each of our subdivided categories
 cell_counts <- prep_data %>% 
-  group_by(age_group, income_group, education_grouped, race, hispan) %>% 
+  group_by(age, household_income_grouped, education_grouped, race_ethnicity, hispanic) %>% 
   summarise(n = n()) #%>%  
 
 
@@ -125,13 +126,13 @@ write_csv(cell_counts, "outputs/post_strat_cellcount.csv")
 #Each will be based on one of our variables of comparison 
 age_prop <- cell_counts %>% 
   ungroup() %>% 
-  group_by(age_group) %>% 
+  group_by(age) %>% 
   mutate(prop = n/sum(n)) %>% 
   ungroup()
 
 income_prop <- cell_counts %>% 
   ungroup() %>% 
-  group_by(income_group) %>% 
[…]

### 2020-11-02 scripts/01-data-cleaning-survey-2.R
Added Optional Data Where Hispanic is removed

@@ -1,0 +1,162 @@
+#### Preamble ####
+# Purpose: The purpose of this code is to prepare and clean the Nationscape Data Set downloaded from the Democracy Fund 
+# Voter Study Group. Because we aren't looking at each and every one of the more than 200 variables included in the dataset,
+# we want to clean the dataset so that it only includes variables that we are interested in. To address this issue, we only
+# included the variables that we are interested in. Also, in our analysis, we will only be looking at who is going to win 
+# the popular vote between Donald Trump and Joe Biden, therefore we cleaned the results so that they only showcase those 
+# willing to vote for Donald Trump or Joe Biden. We also added another variable that was not originally included in the
+# dataset to make vote a binary variable. A problem we encountered with the raw dataset was that a lot of the values were 
+# shown as N/A; to address this issue, we also cleaned the dataset so that it removed all N/A values meaning for each row 
+# in the dataset, every column has a meaningful value.
+# Author: Arjun Dhatt, Ben Draskovic, Gantavya Gupta, Yiqu Ding 
+# Data: 2 November 2020
+# Contact: arjun.dhatt@mail.utoronto.ca 
+# License: MIT
+# Pre-requisites: 
+## 1. Go to: https://www.voterstudygroup.org/publication/nationscape-data-set
+## 2. Look for the 'Download the Full Data Set' heading and enter your information and submit your request. 
+## After a short period of time, you will have received an email containing links to the dataset. 
+## 3. Click on the link included in the email. Under the header 'Download Resources', download the .dta. 
+## files. This will be a zip file, therefore you will have to unzip it.
+## 4. After unzipping the file, open 'phase_2_v20200814' -> 'ns20200625' -> '01-data_cleaning-survey.R'. 
+## We open the folder pertaining to 'ns20200625' because we want data from June 25th, 2020. 
+## 5. We want to then open '01-data_cleaning-survey.R' in R that way we can filter the dataset to our needs. 
+## 6. You may need to adjust the file paths depending on your system. 
+
+
+#### Workspace setup ####
+library(haven)
+library(tidyverse)
+library(dplyr)
+
+# Read in the raw data 
[…]

### 2020-11-02 scripts/01-data_cleaning-post-strat-2.R

@@ -1,0 +1,146 @@
+#### Preamble ####
+# Purpose: To prepare the survey data downloaded from IPUMS USA based on the 2018 ACS survey. 
+# This data set will be used in the post-stratification process. MEaning that the data will be 
+# adjusted to match the categories used in the cleaned Nation-Scape Data set. Then bin counts will
+# be generated so that the two data sets may be compared. 
+# Author: Arjun Dhatt, Ben Draskovic, Gantavya Gupta, Yiqu Ding 
+# Data: 2 November 2020
+# Contact: ben.draskovic@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: 
+# - Need to have downloaded the ACS data and saved it to inputs/ACS
+# - Set up a gitignore in order to retain the privacy of the data 
+
+
+#### Workspace setup ####
+library(haven)
+library(tidyverse)
+library(dplyr)
+# Read in the raw data. 
+raw_data <- read_dta("inputs/ACS/usa_00001.dta.gz"
+)
+# Add the labels
+raw_data <- labelled::to_factor(raw_data)
+
+# Select variables of interest for analysis
+names(raw_data)
+
+reduced_data <- 
+  raw_data %>% 
+  select(age, 
+         race, 
+         educ,
+         ftotinc)
+rm(raw_data)
+
+#Remove all na values from the data (For Family income NA was 9999999)
+#Remove all children under 18
+prep_data <- reduced_data %>% 
+  filter(
+    ftotinc<9999999,
+    as.integer(age)>18,
+    !is.na(age),
+    !is.na(race),
+  )
+# This removes 799,716 respondants from the data 
+
+
+#Group the education responses into groups that best match the groups in UCLA Survey being used
+#Notably an estimate as to when a degree would be completed had to be used for this we used the estimate of 3 years or above
+recode_key_education <- c(  
+  "n/a or no schooling" = "Less than HS",
+  "nursery school to grade 4" = "Less than HS",
+  "grade 5, 6, 7, or 8" = "Less than HS",
+  "grade 9" = "Completed Some HS",
+  "grade 10" = "Completed Some HS",
+  "grade 11" = "Completed Some HS",
+  "grade 12" = "Completed HS",
+  "1 year of college" = "Participated in Higher Education",
+  "2 years of college" = "Participated in Higher Education",
[…]

### 2020-11-02 scripts/01-data-cleaning-survey-2.R
Update

@@ -147,7 +147,7 @@ tbdata <- tbdata %>%
 
 
 
-write_csv(tbdata, "outputs/clean-survey.csv")
+write_csv(tbdata, "outputs/clean-survey-2.csv")
 
 
 #### What else???? ####

### 2020-11-02 outputs/paper/paper.Rmd
Update paper.Rmd

--- 2020-11-02 outputs/paper/paper.Rmd
@@
 
-To mimic the population as closely as possible, we need a post-stratification dataset large enough to refer to. In this report, we use the ACS(reason).
+To mimic the population as closely as possible, we need a post-stratification dataset large enough to refer to.
+In this report, we use the ACS because the census happens less frequently than the ACS which is updated annually.
 
@@
 - 11 education levels
-- 15 races;
+- 7 races;
 - 24 income levels;
@@
 attach(clean_survey)
-mod <- brm(binary ~ age + education_grouped + race_ethnicity + hispanic + household_income_grouped + state + extra_covid_worn_mask,
+mod <- brm(binary ~ (1|age_group) + (1|education_grouped) + (1|race_ethnicity) + (1|household_income_grouped),
            data = clean_survey,
            family = bernoulli(),
-           iter = 4000
+           iter = 4000,
+           control = list(adapt_delta = 0.98)
            )
@@
 summary(mod)
-```
-
-```{r}
-usa_00001$estimate <-
-  mod %>%
-  predict(newdata = usa_00001)
-```
-
-```{r}
-# to get the estimated proportions and associated 95% PIs by state
-res_state <- mod %>%
-  tidybayes::add_predicted_draws(newdata = census_data) %>%
-  rename(president_predict = .prediction) %>%  
-  mutate(president_predict_prop = president_predict*prop) %>% 
-  group_by(state_name, .draw) %>% 
-  summarise(kept_name_predict = sum(kept_name_predict_prop)) %>% 
-  group_by(state_name) %>% 
-  summarise(mean = mean(kept_name_predict), 
-            lower = quantile(kept_name_predict, 0.025), 
-            upper = quantile(kept_name_predict, 0.975))
-```
-
-```{r, eval=FALSE}
-# graph by state
-res_state %>% 
-  arrange(-mean) %>% 
-  left_join(d %>%
-              group_by(state_name, kept_name) %>%
-              summarise(n = n()) %>%
-              group_by(state_name) %>%
-              mutate(prop = n/sum(n)) %>%
-              filter(kept_name==1)) %>% 
-  ggplot(aes(y = mean, x = forcats::fct_inorder(state_name), color = "MRP estimate")) + 
-  geom_point() +
-  coord_flip() + 
-  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0) + 
-  ylab("proportion keeping maiden name") + 
-  xlab("state") + 
-  geom_point(aes(state_name, prop, color = "raw data")) +
-  scale_color_manual(name = "", values = c("MRP estimate" = "black", "raw data" = "red")) + 
-  theme_bw() +
-  ggtitle("Proportion of women keeping maiden name after marriage")
-
-res_state %>% 
-  mutate(statename = str_to_title(state_name)) %>% 
-  #mutate(statename = ifelse(state_name=="district of columbia", "District of Columbia", statename)) %>% 
-  ggplot(aes(fill = mean, state = statename)) + 
-  geom_statebins() +
-  scale_fill_viridis_c(name = "proportion keeping name") +
-  theme_void()
-ggsave("state_plot.png", width = 8, height = 6)
 ```

### 2020-11-02 outputs/paper/paper.Rmd
model glmer()

@@
   bookdown::pdf_document2:
+    fig_caption: yes        
+    includes:  
+      in_header: modify.tex
 toc: FALSE
 bibliography: references.bib
+header-includes:
+- \usepackage{caption}
 ---
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE)
+knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
 library(tidyverse)
@@
 
-- 76 different ages;
-- 11 education levels
-- 7 races;
-- 24 income levels;
-- 51 states;
-- 2 options for mask wearing habits.
+- 4 different age groups;
+- 6 education levels
+- 5 races;
+- 6 income levels;
 
-That is 30,697,920 cells in total. We fit the logistic regressions for estimating candidate support in each cell. We used `function` from `package` to fit \@ref(eq:model).
+That is 720 cells in total. We fit the logistic regressions for estimating candidate support in each cell. We used `function` from `package` to fit \@ref(eq:model).
 
@@
 $\beta_0$ is the intercept,each of $\beta_{j[i]}^{var}$ represents the parameter for the i-th respondent in j-th cell.
-For example, $\beta_{j[i]}^{state}$ can take values from $\beta$ for all states in the US.
-Then the model sums up estimates for each cell to the population.
+For example, $\beta_{j[i]}^{edu}$ can take values from $\beta$ from any of the six education levels.
+Then we predict the results by summing up estimates for each cell to the population.
+The results of the logidtic regression is summarised in table 1.
 
@@
 ```{r}
-attach(clean_survey)
-mod <- brm(binary ~ (1|age_group) + (1|education_grouped) + (1|race_ethnicity) + (1|household_income_grouped),
-           data = clean_survey,
-           family = bernoulli(),
-           iter = 4000,
-           control = list(adapt_delta = 0.98)
+mod <- glmer(binary ~ age_group + (1|education_grouped) + race_ethnicity + household_income_grouped,
+           data = clean_survey_2,
+           family = binomial()
            )
@@
 
+### Summary Table
+\begin{center}
+\captionof{table}{3329}
+\begin{tabular}{|l|l|l|l|}
+\hline
+variable & $\hat{\beta}$ & Std. Error & p-value \\ \hline
+intercept & -0.00 & 0.26 & 0.99 \\ \hline
+$36 < age < 55$ & $0.42$ & $0.07$ & $6.06e^{-9}$ \\ \hline
+$56 < age < 75$ & $0.37$ & $0.07$ & $8.91e^{-7}$ \\ \hline
+$age > 76$ & $0.62$ & $0.18$ & $0.00$ \\ \hline
+Asian or Pacific Islander & $ -0.75 $ & $0.27$ & $0.01$ \\ \hline
+black & $-1.89$ & $0.26$ & $1.25e^{-12}$ \\ \hline
+nec & $-0.75$ & $0.26$ & $0.01$ \\ \hline
+white & $0.09$ & $0.24$ & $0.68$ \\ \hline
+$income > 150k$ & $0.14$ & $0.11$ & $0.22$ \\ \hline
+$income < 25k$ & $-0.38$ & $0.10$ & $0.01$ \\ \hline
+$25k < income < 50k$ & $-0.27$ & $0.10$ & $0.01$ \\ \hline
+$50k < income < 75k$ & $-0.19$ & $0.10$ & $0.06$ \\ \hline
+$75k < income < 100k$ & $-0.31$ & $0.11$ & $0.01$ \\ \hline
+\end{tabular}
+\end{center}
+
 # Discussion
+
+```{r}
+#prediction with posterior_linpred()
+posterior_prob <- posterior_linpred(mod, transform = TRUE, newdata = post_strat_cellcount_2)
+poststrat_prob <- posterior_prob %*% post_strat_cellcount_2$n / sum(post_strat_cellcount_2$n)
+model_popn_pref <- c(mean = mean(poststrat_prob), sd = sd(poststrat_prob))
+round(model_popn_pref, 3)
+```
+
+```{r}
+# predictio using predict()
+post_strat_cellcount_2$estimate <-
+  mod %>%
+  predict(newdata = post_strat_cellcount_2)
+```
+
+```{r}
+# prediction using add_prediction_draw
+post_stratified_estimates <-
+  mod %>%
+  tidybayes::add_predicted_draws(newdata = census_data) %>%
+  rename(alp_predict = .prediction) %>%
+  mutate(alp_predict_prop = alp_predict*cell_prop_of_division_total) %>%
+  group_by(state, .draw) %>%
+  summarise(alp_predict = sum(alp_predict_prop)) %>%
+  group_by(state) %>%
+  summarise(mean = mean(alp_predict),
+  lower = quantile(alp_predict, 0.025),
+  upper = quantile(alp_predict, 0.975))
+```
 

### 2020-11-02 scripts/01-data_cleaning-post-strat-2.R
Re-named Age group

@@ -85,7 +85,7 @@ prep_data <- prep_data %>%
     race_ethnicity = race0,
   ) %>% 
   mutate(
-    age = case_when(
+    age_group = case_when(
       as.numeric(age) >=18 & as.numeric(age) <=35 ~ "18-35",
       as.numeric(age) >=36 & as.numeric(age) <=55 ~ "36-55",
       as.numeric(age) >=56 & as.numeric(age) <=75 ~ "56-75",
@@ -103,7 +103,7 @@ prep_data <- prep_data %>%
     )
   ) %>% 
   select(
-    age, household_income_grouped, education_grouped, race_ethnicity
+    age_group, household_income_grouped, education_grouped, race_ethnicity
   )
 
 
@@ -112,7 +112,7 @@ write_dta(prep_data, "outputs/post_strat_data-2.dta")
 
 #Create a new tibble that includes the count of individuals in each of our subdivided categories
 cell_counts <- prep_data %>% 
-  group_by(age, household_income_grouped, education_grouped, race_ethnicity) %>% 
+  group_by(age_group, household_income_grouped, education_grouped, race_ethnicity) %>% 
   summarise(n = n()) %>% 
   mutate(prop = n/nrow(prep_data))
 

### 2020-11-02 scripts/01-data-cleaning-survey-2.R
Updating the older files with Age_group change

@@ -146,7 +146,6 @@ tbdata <- tbdata %>%
 
 
 
-
 write_csv(tbdata, "outputs/clean-survey-2.csv")
 
 

### 2020-11-02 outputs/paper/paper.Rmd

@@
 ```
+# Abstract
+
+In this report, we will be forecasting the winner of the upcoming US Presidential Elections 2020 between incumbent Donald Trump of the Republican Party and Joe Biden of the Democratic Party, by looking at different factors that affect a citizen’s voting intentions leading to Election Day.
+We cleaned the (name of the dataset) dataset and chose the variables age, education, race, family income, geographic region, and mask-wearing decision which will form the basis of our Elections prediction.
+Then we used a MRP model (a combination of multilevel logistic regression and post-stratification) to analyse the factors and it also helps us in achieving a much narrower confidence interval for our prediction.
+After our analysis, we concluded that (who will win the election) will win x% of the national popular vote, with a y% of margin of error.
 

### 2020-11-02 outputs/paper/paper.Rmd
results updated

--- 2020-11-02 outputs/paper/paper.Rmd
@@
 library(lme4)
-library(rstanarm)
-library(brms)
+library(merTools)
+library(readr)
+library(knitr)
 ```
@@
 ```{r}
+clean_survey_2 <- read_csv("clean-survey-2.csv")
 mod <- glmer(binary ~ age_group + (1|education_grouped) + race_ethnicity + household_income_grouped,
@@
            )
-
-summary(mod)
 ```
@@
 \begin{center}
-\captionof{table}{3329}
+\captionof{table}{statistics summary for logistic regression}
 \begin{tabular}{|l|l|l|l|}
@@
 ```{r}
-#prediction with posterior_linpred()
-posterior_prob <- posterior_linpred(mod, transform = TRUE, newdata = post_strat_cellcount_2)
-poststrat_prob <- posterior_prob %*% post_strat_cellcount_2$n / sum(post_strat_cellcount_2$n)
-model_popn_pref <- c(mean = mean(poststrat_prob), sd = sd(poststrat_prob))
-round(model_popn_pref, 3)
+# Read in the csv file for post stratification
+post_strat_cellcount_2 <- read_csv("~/STA304/Trump-vs-Biden/outputs/post_strat_cellcount-2.csv")
+# get post stratification estimates using predict()
+post_strat_cellcount_2$estimate <-
+  mod %>%
+  predict(newdata = post_strat_cellcount_2, allow.new.level = TRUE, type="response")
 ```
@@
 ```{r}
-# predictio using predict()
-post_strat_cellcount_2$estimate <-
-  mod %>%
-  predict(newdata = post_strat_cellcount_2)
+post_strat_cellcount_2 %>%
+  mutate(president_predict_prop = estimate*prop) %>%
+  group_by(education_grouped) %>%
+  summarise(president_predict = sum(president_predict_prop)) %>% 
+  as.data.frame() %>% 
+  knitr::kable()
 ```
 
-```{r}
-# prediction using add_prediction_draw
-post_stratified_estimates <-
-  mod %>%
-  tidybayes::add_predicted_draws(newdata = census_data) %>%
-  rename(alp_predict = .prediction) %>%
-  mutate(alp_predict_prop = alp_predict*cell_prop_of_division_total) %>%
-  group_by(state, .draw) %>%
-  summarise(alp_predict = sum(alp_predict_prop)) %>%
-  group_by(state) %>%
-  summarise(mean = mean(alp_predict),
-  lower = quantile(alp_predict, 0.025),
-  upper = quantile(alp_predict, 0.975))
+```{r, fig.cap='95% Prediction Intervals for forcasting the Chances that Donald Trump wins the election'}
+PI <- predictInterval(merMod = mod, newdata = post_strat_cellcount_2,                         
+                      level = 0.95, n.sims = 1000,                         
+                      stat = "median", type= "probability",                      
+                      include.resid.var = TRUE)
+
+ggplot(aes(x=1:30, y=fit, ymin=lwr, ymax=upr), data=PI[1:30,]) +   
+  geom_point() +   geom_linerange() +   
+  labs(x="Index", y="Prediction w/ 95% PI") + 
+  theme_bw()
 ```

### 2020-11-02 outputs/paper/paper.Rmd
4.04

@@
 -	household_income
-     o	“What is your current annual household income before taxes? 
+     o	“What is your current annual household income before taxes?" 
      o	Provides an extensive list of options beginning with $5,000 increments and then increases to $25,000 increments
@@
 We also created another variable called ‘binary’ which outputs the result of the variable ‘trump_biden’ as a 1 or a 0 making it binary, therefore easier to analyze.
+[ADD INFORMATOIN ABOUT OTHER MUTATIONS WE CREATED]
 
+```{r}
+incomeinfo <- tbdata %>% group_by(household_income_grouped) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
+incomegraph <- incomeinfo %>% ggplot(aes(x = "", y = prop, fill = household_income_grouped)) + 
+      geom_bar(width = 1, stat = "identity") + 
+      coord_polar("y", start = 0) +
+      scale_fill_brewer(palette = "Accent") +
+      theme_void() +
+      ylab("") + xlab("") + 
+     labs(title = "", fill="Household Income") +
+     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=45, size = 4.7) +
+     theme(text = element_text(size=15))
+incomegraph
+```
+
+```{r}
+raceinfo <- tbdata %>% group_by(race_ethnicity) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
+racegraph <- raceinfo %>% ggplot(aes(x = "", y = prop, fill = race_ethnicity)) + 
+      geom_bar(width = 1, stat = "identity") + 
+      coord_polar("y", start = 0) +
+      scale_fill_brewer(palette = "Set3") +
+      theme_void() +
+      ylab("") + xlab("") + 
+     labs(title = "", fill="What is your race?") +
+     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=45, size = 4) +
+     theme(text = element_text(size=13))
+racegraph
+```
+
+```{r}
+educationinfo <- tbdata %>% group_by(education_grouped) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
+educationgraph <- educationinfo %>% ggplot(aes(x = "", y = prop, fill = education_grouped)) + 
+      geom_bar(width = 1, stat = "identity") + 
+      coord_polar("y", start = 0) +
+      scale_fill_brewer(palette = "Set2") +
+      theme_void() +
+      ylab("") + xlab("") + 
+     labs(title = "", fill="Education") +
+     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=45, size = 4) +
+     theme(text = element_text(size=15))
+educationgraph
+```
+
+```{r}
+ageinfo <- tbdata %>% group_by(age_group) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
+agegraph <- ageinfo %>% ggplot(aes(x = "", y = prop, fill = age_group)) + 
+      geom_bar(width = 1, stat = "identity") + 
+      coord_polar("y", start = 0) +
+      scale_fill_brewer(palette = "Set3") +
+      theme_void() +
+      ylab("") + xlab("") + 
+     labs(title = "", fill="Age Groups") +
+     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=45, size = 4)+
+     theme(text = element_text(size=13))
+agegraph
+```
 Key features of data?

### 2020-11-02 outputs/paper/paper.Rmd
4.07
6.31

@@
 # Introduction
+
+The US 2020 Election is considered by many to be one of the most crucial elections in recent history.
+American voters will be deciding to elect Democratic Leader, Joe Biden or Republican leader, Donald Trump.
+In this report, we will be forecasting the results of the US 2020 election using multi-level regression with post stratification.
+
+We are interested in finding out who will win the overall popular vote in the US 2020 election between Donald Trump and Joe Biden.
+To begin, we started by cleaning the dataset provided by Nationscape.
+The data we are using was collected from June 25th, 2020 to July 1st, 2020.
+Using the dataset, we plan to closely analyze the following variables to use them as predictors in predicting the results of the 2020 US election:
+-	X
+-	X
+-	X
+-	X
+After using multi-level regression with post stratification, we determined that Joe Biden will be the winner of the US 2020 Election.
+Predicting the results of the US 2020 election is important because it helps give those residing in the USA certainty about who their next president will be.
+Information about the winner of the election is highly sought after because it can be used to predict upcoming policy.
+This is useful for individuals and organizations when planning their lives and can have a large impact on the rights of some individuals.
+Additionally, collecting information related to the election allows us to analyze different demographic groups and determine how they are voting to further identify areas they find important; this information is important from a policy design perspective and also to analyze how society is interacting.
+
+In this report, we will begin by ____ [Outline Structure of report].
 
@@
 
+The first 6 rows of the dataset can be viewed below: 
+```{r}
+head(tbdata)
+```
+
 ```{r}
@@
 Key features of data?
+
+```{r}
+head(tbdata)
+```
 

### 2020-11-03 scripts/01-data-cleaning-survey.R
7.51

@@ -5,9 +5,11 @@
 # included the variables that we are interested in. Also, in our analysis, we will only be looking at who is going to win 
 # the popular vote between Donald Trump and Joe Biden, therefore we cleaned the results so that they only showcase those 
 # willing to vote for Donald Trump or Joe Biden. We also added another variable that was not originally included in the
-# dataset to make vote a binary variable. A problem we encountered with the raw dataset was that a lot of the values were 
-# shown as N/A; to address this issue, we also cleaned the dataset so that it removed all N/A values meaning for each row 
-# in the dataset, every column has a meaningful value.
+# dataset to make vote a binary variable. To adress issues with some variables containing an excessive amount of options 
+# (e.g. age, education etc.) we created additional variables that would group the values of the variable so that they are 
+# easier to analyze A problem we encountered with the raw dataset was that a lot of the values were shown as N/A; to address
+# this issue, we also cleaned the dataset so that it removed all N/A values meaning for each row in the dataset, every column 
+# has a meaningful value.
 # Author: Arjun Dhatt, Ben Draskovic, Gantavya Gupta, Yiqu Ding 
 # Data: 2 November 2020
 # Contact: arjun.dhatt@mail.utoronto.ca 
@@ -177,6 +179,7 @@ write_csv(tbdata, "outputs/clean-survey.csv")
 # Maybe make some as.numeric(age)-groups?
 # Maybe check the values?
 # Is vote a binary? If not, what are you going to do?
+
 
 
 # The vote is not a binary variable, it contains 758 "Don't Know", 2626 "Donald Trump", 3075 "Joe Biden" and 20 NAs. 

### 2020-11-03 scripts/01-data-cleaning-survey.R
7.54

@@ -56,7 +56,7 @@ tbdata <-
 # NA value. 
 tbdata <- na.omit(tbdata)
 
-#Group all of the Asian and PAcific Islander Ethnicity options in to 3 categories
+#Group all of the Asian and Pacific Islander Ethnicity options in to 3 categories to make it easier to analyze
 recode_key_race <- c(  
   "Asian (Asian Indian)" = "asian or pacific islander",
   "Asian (Chinese)" = "asian or pacific islander",
@@ -78,7 +78,7 @@ recode_key_race <- c(
 # After the key is made use the recode function to create a new string based on the collumn being changed 
 race_ethnicity0 <- recode(tbdata$race_ethnicity, !!!recode_key_race)
 
-#Group the incomes in to groups that are easier to display
+#Group income so that it is easier to analyze. 
 recode_key_income <- c(  
   "Less than $14,999" = "$25k or less",
   "$15,000 to $19,999" = "$25k or less",
@@ -174,15 +174,7 @@ tbdata <- tbdata %>%
 
 write_csv(tbdata, "outputs/clean-survey.csv")
 
-
-#### What else???? ####
-# Maybe make some as.numeric(age)-groups?
-# Maybe check the values?
-# Is vote a binary? If not, what are you going to do?
-
-
-
-# The vote is not a binary variable, it contains 758 "Don't Know", 2626 "Donald Trump", 3075 "Joe Biden" and 20 NAs. 
+# Vote is not a binary variable in our data. It contains 758 "Don't Know", 2626 "Donald Trump", 3075 "Joe Biden" and 20 NAs. 
 # We resolved this by deleting the "Don't know" and NA responses, since it was a relatively small (12%) part of our
-# data set.
+# data set. This makes the dataset much simpler and easier to analyze. 
 

### 2020-11-03 outputs/paper/paper.Rmd
8.01

@@
 In this report, we will be forecasting the winner of the upcoming US Presidential Elections 2020 between incumbent Donald Trump of the Republican Party and Joe Biden of the Democratic Party, by looking at different factors that affect a citizen’s voting intentions leading to Election Day.
-We cleaned the (name of the dataset) dataset and chose the variables age, education, race, family income, geographic region, and mask-wearing decision which will form the basis of our Elections prediction.
-Then we used a MRP model (a combination of multilevel logistic regression and post-stratification) to analyse the factors and it also helps us in achieving a much narrower confidence interval for our prediction.
-After our analysis, we concluded that (who will win the election) will win x% of the national popular vote, with a y% of margin of error.
+We cleaned the Nationscape dataset and chose the variables age, education, race, family income, geographic region, and mask-wearing decision which will form the basis of our Elections prediction.
+Then we used an MRP model (a combination of multilevel logistic regression and post-stratification) to analyse the factors and it also helps us in achieving a much narrower confidence interval for our prediction.
+After our analysis, we concluded that Joe Biden will win the overall popular vote of the 2020 American presidential election.
 
@@
 
-In this report, we will begin by ____ [Outline Structure of report].
+In this report, we will begin by discussing the data and then modeling our results. Lastly, we will discuss the results of our analysis and include an appendix.
 
@@
 ```{r}
+# Setup data for the pie chart and mutate a variable that details proportions for various responses. 
 incomeinfo <- tbdata %>% group_by(household_income_grouped) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
+# Graph the pie chart using ggplot; Set colour scheme; font, etc. 
 incomegraph <- incomeinfo %>% ggplot(aes(x = "", y = prop, fill = household_income_grouped)) + 

### 2020-11-03 outputs/paper/paper.Rmd
8.10

@@
 
-We also created another variable called ‘binary’ which outputs the result of the variable ‘trump_biden’ as a 1 or a 0 making it binary, therefore easier to analyze.
-[ADD INFORMATOIN ABOUT OTHER MUTATIONS WE CREATED]
+We created an additional variable called ‘binary’ which outputs the result of the variable ‘trump_biden’ as a 1 or a 0 making it binary, therefore easier to analyze.
+Since some variables had an extensive list of options (e.g.
+age, household income), we grouped the responses so that they are simpler and easier to analyze.
 
-The first 6 rows of the dataset can be viewed below: 
+The first few rows of the cleaned dataset can be viewed below: 
 ```{r}
@@
 incomeinfo <- tbdata %>% group_by(household_income_grouped) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
-# Graph the pie chart using ggplot; Set colour scheme; font, etc. 
+# Graph the pie chart using ggplot; Set colour scheme, font, etc. 
 incomegraph <- incomeinfo %>% ggplot(aes(x = "", y = prop, fill = household_income_grouped)) + 
@@
      geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=45, size = 4.7) +
-     theme(text = element_text(size=15))
+     theme(text = element_text(size=13))
 incomegraph
@@
 ```{r}
+# Setup data for the pie chart and mutate a variable that details proportions for various responses. 
 raceinfo <- tbdata %>% group_by(race_ethnicity) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
+# Graph the pie chart using ggplot; Set colour scheme, font, etc. 
 racegraph <- raceinfo %>% ggplot(aes(x = "", y = prop, fill = race_ethnicity)) + 
@@
 ```{r}
+# Setup data for the pie chart and mutate a variable that details proportions for various responses. 
 educationinfo <- tbdata %>% group_by(education_grouped) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
+# Graph the pie chart using ggplot; Set colour scheme, font, etc. 
 educationgraph <- educationinfo %>% ggplot(aes(x = "", y = prop, fill = education_grouped)) + 
@@
      geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=45, size = 4) +
-     theme(text = element_text(size=15))
+     theme(text = element_text(size=13))
 educationgraph
@@
 ```{r}
+# Setup data for the pie chart and mutate a variable that details proportions for various responses. 
 ageinfo <- tbdata %>% group_by(age_group) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
+# Graph the pie chart using ggplot; Set colour scheme, font, etc. 
 agegraph <- ageinfo %>% ggplot(aes(x = "", y = prop, fill = age_group)) + 
@@
 ```
+
 Key features of data?
-
-```{r}
-head(tbdata)
-```
 

### 2020-11-03 outputs/paper/paper.Rmd
8.12

@@
      labs(title = "", fill="Household Income") +
-     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=45, size = 4.7) +
+     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=0, size = 4.7) +
      theme(text = element_text(size=13))
@@
      labs(title = "", fill="Education") +
-     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=45, size = 4) +
+     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=0, size = 4) +
      theme(text = element_text(size=13))
@@
      labs(title = "", fill="Age Groups") +
-     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=45, size = 4)+
+     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=0, size = 4)+
      theme(text = element_text(size=13))

### 2020-11-03 outputs/paper/paper.Rmd
8.29

@@
 
-Key features of data?
+The dataset that we used contains many key features.
+For one, a lot of the variables contain an extensive list of options assuring us that the data represents the participant's view accurately.
+Despite the fact that we cleaned the dataset to make it simpler to view, we still believe that the detailed responses that the participants provided accurately reflect their views on the 2020 election.
+Another key feature is
 

### 2020-11-03 outputs/paper/paper.Rmd
8.38

--- 2020-11-03 outputs/paper/paper.Rmd
@@
 Since some variables had an extensive list of options (e.g.
-age, household income), we grouped the responses so that they are simpler and easier to analyze.
+age, household income), we grouped the responses for those variables so that they are simpler and easier to analyze.
 
@@
      labs(title = "", fill="What is your race?") +
-     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=45, size = 4) +
+     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=0, size = 3) +
      theme(text = element_text(size=13))
@@
 
-Key features of data?
+The dataset that we used contains many key features.
+Many of the variables in the dataset contain an extensive list of options assuring us that the data represents the participant's view accurately.
+Despite the fact that we cleaned the dataset to make it simpler to view, we still believe that the detailed responses that the participants provided accurately reflect their views on the 2020 election, making our analysis meaningful.
+Another key feature is the fact that the data was collected over a short period of time— from June 25th, 2020 to July 1st, 2020.
+This significantly reduces the negative time based effects that may have affected the data ensuring that all respondents are responding on a similar ground and no one's opinion dramatically differed due to the survey taking place over a large period of time.
 

### 2020-11-03 outputs/paper/paper.Rmd
Moving some stuff

--- 2020-11-03 outputs/paper/paper.Rmd
@@
 library(tidyverse)
+library(dplyr)
 library(lme4)
@@
 In this report, we will be forecasting the winner of the upcoming US Presidential Elections 2020 between incumbent Donald Trump of the Republican Party and Joe Biden of the Democratic Party, by looking at different factors that affect a citizen’s voting intentions leading to Election Day.
-We cleaned the Nationscape dataset and chose the variables age, education, race, family income, geographic region, and mask-wearing decision which will form the basis of our Elections prediction.
-Then we used an MRP model (a combination of multilevel logistic regression and post-stratification) to analyse the factors and it also helps us in achieving a much narrower confidence interval for our prediction.
-After our analysis, we concluded that Joe Biden will win the overall popular vote of the 2020 American presidential election.
+We cleaned the (name of the dataset) dataset and chose the variables age, education, race, family income, geographic region, and mask-wearing decision which will form the basis of our Elections prediction.
+Then we used a MRP model (a combination of multilevel logistic regression and post-stratification) to analyse the factors and it also helps us in achieving a much narrower confidence interval for our prediction.
+After our analysis, we concluded that (who will win the election) will win x% of the national popular vote, with a y% of margin of error.
 
 # Introduction
-
-The US 2020 Election is considered by many to be one of the most crucial elections in recent history.
-American voters will be deciding to elect Democratic Leader, Joe Biden or Republican leader, Donald Trump.
-In this report, we will be forecasting the results of the US 2020 election using multi-level regression with post stratification.
-
-We are interested in finding out who will win the overall popular vote in the US 2020 election between Donald Trump and Joe Biden.
-To begin, we started by cleaning the dataset provided by Nationscape.
-The data we are using was collected from June 25th, 2020 to July 1st, 2020.
-Using the dataset, we plan to closely analyze the following variables to use them as predictors in predicting the results of the 2020 US election:
--	X
--	X
--	X
--	X
-After using multi-level regression with post stratification, we determined that Joe Biden will be the winner of the US 2020 Election.
-Predicting the results of the US 2020 election is important because it helps give those residing in the USA certainty about who their next president will be.
-Information about the winner of the election is highly sought after because it can be used to predict upcoming policy.
-This is useful for individuals and organizations when planning their lives and can have a large impact on the rights of some individuals.
-Additionally, collecting information related to the election allows us to analyze different demographic groups and determine how they are voting to further identify areas they find important; this information is important from a policy design perspective and also to analyze how society is interacting.
-
-In this report, we will begin by discussing the data and then modeling our results. Lastly, we will discuss the results of our analysis and include an appendix.
 
@@
 
-We created an additional variable called ‘binary’ which outputs the result of the variable ‘trump_biden’ as a 1 or a 0 making it binary, therefore easier to analyze.
-Since some variables had an extensive list of options (e.g.
-age, household income), we grouped the responses so that they are simpler and easier to analyze.
+We also created another variable called ‘binary’ which outputs the result of the variable ‘trump_biden’ as a 1 or a 0 making it binary, therefore easier to analyze.
+[ADD INFORMATOIN ABOUT OTHER MUTATIONS WE CREATED]
 
-The first few rows of the cleaned dataset can be viewed below: 
+The first 6 rows of the dataset can be viewed below: 
 ```{r}
-head(tbdata)
+Table1 <- tbdata %>% 
+  select(age_group, household_income_grouped, race_ethnicity, trump_biden) %>% 
+  head() %>% 
+  kable(align = "c",
+        format = "simple",
+        col.names = c("Age", "Sex", "Have Children", "Age", 
+                      "Family Income", "Education Level", "Urban / Rural"),
+        ) %>% 
+  kable_styling(font_size = 5)
 ```
@@
 ```{r}
-# Setup data for the pie chart and mutate a variable that details proportions for various responses. 
 incomeinfo <- tbdata %>% group_by(household_income_grouped) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
-# Graph the pie chart using ggplot; Set colour scheme, font, etc. 
 incomegraph <- incomeinfo %>% ggplot(aes(x = "", y = prop, fill = household_income_grouped)) + 
@@
      labs(title = "", fill="Household Income") +
-     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=0, size = 4.7) +
-     theme(text = element_text(size=13))
+     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=45, size = 4.7) +
+     theme(text = element_text(size=15))
 incomegraph
@@
 ```{r}
-# Setup data for the pie chart and mutate a variable that details proportions for various responses. 
 raceinfo <- tbdata %>% group_by(race_ethnicity) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
-# Graph the pie chart using ggplot; Set colour scheme, font, etc. 
 racegraph <- raceinfo %>% ggplot(aes(x = "", y = prop, fill = race_ethnicity)) + 
@@
 ```{r}
-# Setup data for the pie chart and mutate a variable that details proportions for various responses. 
 educationinfo <- tbdata %>% group_by(education_grouped) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
-# Graph the pie chart using ggplot; Set colour scheme, font, etc. 
 educationgraph <- educationinfo %>% ggplot(aes(x = "", y = prop, fill = education_grouped)) + 
@@
      labs(title = "", fill="Education") +
-     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=0, size = 4) +
-     theme(text = element_text(size=13))
+     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=45, size = 4) +
+     theme(text = element_text(size=15))
 educationgraph
@@
 ```{r}
-# Setup data for the pie chart and mutate a variable that details proportions for various responses. 
 ageinfo <- tbdata %>% group_by(age_group) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
-# Graph the pie chart using ggplot; Set colour scheme, font, etc. 
 agegraph <- ageinfo %>% ggplot(aes(x = "", y = prop, fill = age_group)) + 
@@
      labs(title = "", fill="Age Groups") +
-     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=0, size = 4)+
+     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=45, size = 4)+
      theme(text = element_text(size=13))
@@
 ```
+Key features of data?
 
-Key features of data?
+```{r}
+head(tbdata)
+```
 

### 2020-11-03 outputs/paper/paper.Rmd

--- 2020-11-03 outputs/paper/paper.Rmd
@@
 ```{r}
-head(tbdata)
+Table1 <- tbdata %>% 
+  select(age_group, household_income_grouped, race_ethnicity, trump_biden) %>% 
+  head() %>% 
+  kable(align = "c",
+        format = "simple",
+        col.names = c("Age", "Sex", "Have Children", "Age", 
+                      "Family Income", "Education Level", "Urban / Rural"),
+        ) %>% 
+  kable_styling(font_size = 5)
 ```

### 2020-11-03 outputs/paper/paper.Rmd
9.22

--- 2020-11-03 outputs/paper/paper.Rmd
@@
 
+In Figure [] below, we can see that the distribution is largely skewed towards families with income less than $50,000:
 ```{r}
@@
 ```
+Because of the skewed distribution of income, we can justify using post stratification.
+Clearly, those with income less than $50,000 are overrepresented in the dataset as they take up 50% of the responses, therefore it is appropriate to use post stratification.
 
+We can see a similar skewed distribution in Figure [] below: 
 ```{r}
@@
 ```
+Looking at the distribution of race, we can see that 75% of the respondants from the survey are white. Since the distribution does not represent minorities, we can justify using post stratification.
 
@@
 
+Lastly, in Figure [] below, we can see how the population aged older than 76 are barely represented: 
 ```{r}
@@
 ```
+The fact that those age 76+ make up only a 3% of the data could be a product of the fact that the survey was completed online.
+Clearly, the survey doesn't accurately represent those aged older than 76 posing the question — does our data represent the United States?
+The answer is no.
+To adjust for the fact that the population aged 76+, we will use post stratification.
 

### 2020-11-03 outputs/paper/paper.Rmd
Added Discussion

--- 2020-11-03 outputs/paper/paper.Rmd
@@
 ```{r}
-Table1 <- tbdata %>% 
-  select(age_group, household_income_grouped, race_ethnicity, trump_biden) %>% 
+tbdata <- read.csv("clean-survey-2.csv")
+tbdatashort <- tbdata %>% 
+  dplyr::select(
+    age_group, race_ethnicity, household_income_grouped, trump_biden
+  )
+Table1 <- tbdatashort %>% 
   head() %>% 
@@
         format = "simple",
-        col.names = c("Age", "Sex", "Have Children", "Age", 
-                      "Family Income", "Education Level", "Urban / Rural"),
+        col.names = c("Age Group", "Race", "Household Income", "Presidential choice")
         ) %>% 
   kable_styling(font_size = 5)
+Table1
 ```
@@
       ylab("") + xlab("") + 
-     labs(title = "", fill="Household Income") +
-     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=0, size = 4.7) +
-     theme(text = element_text(size=13))
+     labs(title = "Survey Distribution of Household Income", fill="Household Income") +
+     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=45, size = 4.7) +
+     theme(text = element_text(size=15))
 incomegraph
@@
       ylab("") + xlab("") + 
-     labs(title = "", fill="What is your race?") +
-     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=0, size = 3) +
+     labs(title = "Survey Distribution of Respondent Race", fill="What is your race?") +
+     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=45, size = 4) +
      theme(text = element_text(size=13))
 racegraph
-```
-
-```{r}
-# Setup data for the pie chart and mutate a variable that details proportions for various responses. 
-educationinfo <- tbdata %>% group_by(education_grouped) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
-# Graph the pie chart using ggplot; Set colour scheme, font, etc. 
-educationgraph <- educationinfo %>% ggplot(aes(x = "", y = prop, fill = education_grouped)) + 
-      geom_bar(width = 1, stat = "identity") + 
-      coord_polar("y", start = 0) +
-      scale_fill_brewer(palette = "Set2") +
-      theme_void() +
-      ylab("") + xlab("") + 
-     labs(title = "", fill="Education") +
-     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=0, size = 4) +
-     theme(text = element_text(size=13))
-educationgraph
 ```
@@
       ylab("") + xlab("") + 
-     labs(title = "", fill="Age Groups") +
-     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=0, size = 4)+
+     labs(title = "Survey Distribution of Respondent Age", fill="Age Groups") +
+     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=45, size = 4)+
      theme(text = element_text(size=13))
@@
 # Read in the csv file for post stratification
-post_strat_cellcount_2 <- read_csv("~/STA304/Trump-vs-Biden/outputs/post_strat_cellcount-2.csv")
+post_strat_cellcount_2 <- read_csv("post_strat_cellcount-2.csv")
 # get post stratification estimates using predict()
@@
 
-## First discussion point
+Weighing the model is important due to the survey collection weakness listed earlier in this paper.
+Survey weaknesses such as voluntary biases, which could see only those who can afford to spend time on a survey filling it out.
+Also, survey access, which would be affected by tech access, tech literacy, and literacy in general as the survey was only written and distributed via online ads.
 
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
+This can be seen in how our demographic values compared to estimated national demographic values.
 
-## Second discussion point
+Before comparing those numbers how, was this analysis weighted?
+The method used for this was MRP or Multi-level Regression with Post-Stratification.
+This methodology was discussed in further detail above.
+But of note the data used for this weighting process was received through the IPUMS USA service.
+Specifically, their repository of American Community Surveys collected by the U.S.
+Census Bureau.
+The data was from the 2018 ACS.
+This survey is a 1-100 national random sampling survey of all U.S.
+addresses within communities of 65,000 people or more.
+It is run over the full 12-month period of the year and received 3.214 million responses for the year of 2018 (U.S.
+Census Bureau 2019).
+While there are some sampling errors in the data they have been weighted across multiple years and the immense sample size helps to keep the risk of error low.
+Looking at a Confidence Interval calculation based on the sample size of 3.214 million and the U.S.
+population in 2018 of 327.2 million if looking at a confidence level of 99% the Confidence Interval is only 0.45 of a percent (CRS 2020).
+Meaning that there is a 99% certainty that the predicted percentage values of the ACS is with in 0.45% of the population value.
 
-## Third discussion point
+For more information on the ACS the user guide can be found in the input folder of the attached git repository.
+
+However, to continue this discussion let’s begin the comparison.
+
+Looking at the income break down of our data it is clear when comparing Figure 1 and Figure 4 that the surveyed population tended towards a lower income on average.
+This is an interesting occurrence and may have to do with the tech literacy having a larger survey biasing effect than literacy and tech access.
+On average older individuals have higher incomes so it could be that the data is skewing younger and that is what is causing this.
+## Figure 1
+```{r}
+incomegraph
+```
+
+## Figure 4
+```{r}
+acs <- read_dta("post_strat_data-2.dta")
+acs <- labelled::to_factor(acs)
+incomeinfoacs <- acs %>% group_by(household_income_grouped) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
+incomegraphacs <- incomeinfoacs %>% ggplot(aes(x = "", y = prop, fill = household_income_grouped)) + 
+      geom_bar(width = 1, stat = "identity") + 
+      coord_polar("y", start = 0) +
+      scale_fill_brewer(palette = "Accent") +
+      theme_void() +
+      ylab("") + xlab("") + 
+     labs(title = "ACS Distribution of Household Income", fill="Household Income") +
+     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=45, size = 4.7) +
+     theme(text = element_text(size=15))
+
+incomegraphacs
+```
+
+Examining the age group, we see that this could certainly be the case.
+As the Surveyed population is significantly younger than the general population.
+Most likely playing into the effects of tech literacy among older generations.
+This can be clearly seen in Figure 2 and 5, where 18-35-year-old respondents are greatly overestimated and 76 and older respondents greatly under-represented.
+
+## Figure 2
+```{r}
+agegraph
+```
+
+## Figure 5
+```{r}
+ageinfoacs <- acs %>% group_by(age_group) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
+agegraphacs <- ageinfoacs %>% ggplot(aes(x = "", y = prop, fill = age_group)) + 
+      geom_bar(width = 1, stat = "identity") + 
+      coord_polar("y", start = 0) +
+      scale_fill_brewer(palette = "Accent") +
+      theme_void() +
+      ylab("") + xlab("") + 
+     labs(title = "ACS Distribution of Respondent Age", fill="Household Income") +
+     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=45, size = 4.7) +
+     theme(text = element_text(size=15))
+
+agegraphacs
+```
+
+Finally, when looking in to the ethnic and racial breakdown of the survey data African American are underrepresented and White Americans overrepresented.
+This is displayed in Figure 3 and 6.
+This could be for a myriad of reasons, but it could be linked to tech access as a higher portion of African Americans experience poverty when compared to their White counterparts.
+
+## Figure 3
+```{r}
+racegraph
+```
+
+## Figure 6
+```{r}
+raceinfoacs <- acs %>% group_by(race_ethnicity) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
+racegraphacs <- raceinfoacs %>% ggplot(aes(x = "", y = prop, fill = race_ethnicity)) + 
+      geom_bar(width = 1, stat = "identity") + 
+      coord_polar("y", start = 0) +
+      scale_fill_brewer(palette = "Accent") +
+      theme_void() +
+      ylab("") + xlab("") + 
+     labs(title = "ACS Distribution of Respondent Race", fill="Household Income") +
+     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=45, size = 4.7) +
+     theme(text = element_text(size=15))
+
+racegraphacs
+```
+
+By separating all respondents of the ACS into subgroups based upon our independent variables we can then create proportions.
+This allows for the weighting of data through the model and adjusts our sample in order to account for the skewed demographics.
+An example of these proportions is displayed below.
+
+## Table 6
+```{r}
+Table6 <- post_strat_cellcount_2 %>% 
+  dplyr::select(
+    age_group, race_ethnicity, household_income_grouped, n, prop
+  ) %>% 
+  head() %>% 
+  kable(align = "c",
+        format = "simple",
+        col.names = c("Age Group", "Race", "Household Income", "Number of Repondents", "Proportion of Responses"),
+        digits = 6
+        ) %>% 
+  kable_styling(font_size = 5)
+Table6
+```
+
+Once the data is adjusted what are the findings?
+
+Based on adjusted values Biden is projected to win the popular vote by a significant margin, ……… This holds true and follows other surveys conducted in this time period (Financial times 2020).
+
+Significantly though the data of this analysis shows a few key demographic group differences in voting patterns.
+
+Firstly, race was a highly significant factor in voting behavior for non-white Americans.
+White Americans were not significantly influenced by there race and tended to vote based on other factors.
+But individuals who described themselves as Black, Asian, a Pacific Islander, or another race all were significantly more likely to vote for Joe Biden than Donald Trump.
+The largest of these effects was among African Americans.
+Compared even to Asian Americans their coefficient was twice as large, meaning they were affected by racial effects twice as much.
+
+```{r include=FALSE}
+aggregate(tbdata[8], list(tbdata$race_ethnicity), mean)
+
+```
+
+Only 12.5% of Black respondents intended to vote for trump.
+
+This aversion from non-white voters makes sense and may not necessarily be tied to a difference in policy opinion.
+Trump has time and time again been caught in racially charged situations where he has displayed disrespect to non-white communities.
+Either in calling African Nations “Shithole Countries” (Sorkin 2018), being resistant to denouncing white supremacist groups that endanger non-white Americans (Bump 2020), or in his reaction the Black Lives Matter movement (Liptak 2020).
+
+So, it is no surprise that race has become a powerful factor on voting for people of color who may feel more strongly threatened than in other Presidential elections.
+
+Secondly, age plays a significant effect.
+It is an oft said adage that the old are more conservative than the young.
+“If it ain’t broke don’t fix it.” This adage appears to hold true for this presidential election as it has for many before it.
+The eldest in the population are far more likely than the young to vote for Trump than Biden.
+However, something of note is those aged 36-55 are slightly more likely to vote trump than those aged 56-75.
+
+This is an interesting trend that is not often a part of election data and deserves further investigation.
+Some possible effects that could be hidden in this data is a worry for retirement as those approaching retirement age worry about whether retirement programs will still exist in the same capacity as they age into them.
+Or it could represent the effect the Covid pandemic is having on this election.
+Those who are older are at higher risk and will on average no more people who are at higher risk.
+So, it could be that people in the 56-75 age range are more worried about Trump’s response to Covid which has been widely criticized.
+So, their age is playing less of a role than their opinion on health care.
+
+Thirdly, income plays a significant effect on voting until an individual begins making over $150k.
+Then the effect begins to weaken.
+Looking at the data there is a clear trend that lower income individuals tend to prefer Biden to Trump.
+With a very linear relationship up until looking at individuals who live in households that make $75k to $100k.
+Where there is a sudden uptick in Biden support before it drops back down.
+And those making $100k and more tend to lean more towards Trump.
+
+There are tow interesting trends in this data.
+First the uptick at $75k is interesting.
+Could this be an uptick from the confounding variable of Education as college educated individuals tend to be more liberal?
+Or is there another confounding variable that is affecting this uptick in Biden support like certain policies aimed at benefiting the middle class?
+Second the significance of the effect income has is strongest at lower incomes but weakens at higher income.
+Could this represent the general need for government support those with lower income experience?
+Meaning that those at lower income are more invested in policies that effect their incomes, than those with higher income.
+Or is this based on confounding variables that begin to exist at higher levels of income like education?
 

### 2020-11-03 outputs/paper/paper.Rmd

@@
 ```
+Looking at the distribution of race, we can see that 75% of the respondants from the survey are white. Since the distribution does not represent minorities, we can justify using post stratification.
 
+Lastly, in Figure [] below, we can see how the population aged older than 76 are barely represented: 
 ```{r}

### 2020-11-03 outputs/paper/paper.Rmd
10.43

--- 2020-11-03 outputs/paper/paper.Rmd
@@
 date: "`r format(Sys.time(), '%d %B %Y')`"
-abstract: |
-  | First sentence. Second sentence. Third sentence. Fourth sentence. 
 output:
@@
 library(knitr)
+library(haven)
 ```
@@
 In this report, we will be forecasting the winner of the upcoming US Presidential Elections 2020 between incumbent Donald Trump of the Republican Party and Joe Biden of the Democratic Party, by looking at different factors that affect a citizen’s voting intentions leading to Election Day.
-We cleaned the Nationscape dataset and chose the variables age, education, race, family income, geographic region, and mask-wearing decision which will form the basis of our Elections prediction.
+We cleaned the Nationscape dataset and closely examine the variables age, race, household income, and vote which will form the basis of our election prediction.
 Then we used an MRP model (a combination of multilevel logistic regression and post-stratification) to analyse the factors and it also helps us in achieving a much narrower confidence interval for our prediction.
@@
 
+# Keywords
+- Forecasting
+- US 2020 Election
+- Multi-level Regression with Post-Stratification
+- Trump
+- Biden
+
 # Introduction
 
-The US 2020 Election is considered by many to be one of the most crucial elections in recent history.
+The United States 2020 Presidential Election is considered by many to be one of the most crucial elections in recent history.
 American voters will be deciding to elect Democratic Leader, Joe Biden or Republican leader, Donald Trump.
@@
 Using the dataset, we plan to closely analyze the following variables to use them as predictors in predicting the results of the 2020 US election:
--	X
--	X
--	X
--	X
+
+-	age (discloses age of respondent)
+-	race_ethnicity (discloses race of respondent)
+-	household_income (discloses household income of respondent)
+-	trump_biden (discloses who the respondent will vote for in the 2020 election)
+
 After using multi-level regression with post stratification, we determined that Joe Biden will be the winner of the US 2020 Election.
@@
 
-In this report, we will begin by discussing the data and then modeling our results. Lastly, we will discuss the results of our analysis and include an appendix.
+In this report, we will begin by discussing with a detailed look at the dataset we are analyzing, followed by a look at the modeling of our results.
+Lastly, we will discuss the results of our analysis and also include an appendix to display any extraneous information.
 
@@
 The variables that we used in our dataset are as follow:
+
 - age
-     o	“What is your age”
+     o	Asks the question “What is your age?”
      o	It provides an integer value greater than or equal to 18 
--	education
-     o	“What is the highest level of education you have completed?” 
-     o	An extensive list of options are provided
--	Hispanic
-     o	“Are you of Hispanic, Latino, or Spanish origin?” 
-     o	An extensive list of options are provided 
 - household_income
-     o	“What is your current annual household income before taxes?" 
-     o	Provides an extensive list of options beginning with $5,000 increments and then increases to $25,000 increments
+     o	Asks the question “What is your current annual household income before taxes?" 
+     o	Provides an extensive list of options beginning with $5,000 increments and then increases to $25,000 increments.
+We         later grouped the options into larger bins making it simpler to understand and easier to analyze
      o	This is the variable in our dataset that many people did not feel comfortable answering and was left as N/A.
@@
 - race_ethnicity
-     o	“What is your race”
-     o	An extensive list of options are provided. 
--	extra_covid_worn_mask
-     o	“Have you done any of the following in the past week? - Worn a mask when going out in public” 
-     o	Yes or No options are available for the respondent to fill out 
--	state
-     o	“Respondent’s state, as a two-character postal abbreviation. Calculated based on entered ZIP code.” 
-     o	Manually filled out by respondent 
+     o	Asks the question “What is your race?”
+     o	An extensive list of options are provided for the respondent to disclose their race.
+Because the list is very               extensive, we decided to group the options into larger bins making to simpler to understand and easier to analyze.
 - trump_biden
-     o	“If the general election for president of the United States was a contest between Joe Biden and Donald Trump, who        would you support? “ 
+     o	Asks the question “If the general election for president of the United States was a contest between Joe Biden and           Donald Trump, who would you support? “ 
      o	Options are either ‘Joe Biden’, ‘Donald Trump’, or ‘Don’t Know’
@@
 Since some variables had an extensive list of options (e.g.
-age, household income), we grouped the responses for those variables so that they are simpler and easier to analyze.
+age, household income, race), we grouped the responses for those variables so that they are simpler and easier to analyze.
+
+To develop a sense of familiarity with the dataset, we will closely examine some of the variables we will be analyzing in the dataset.
 
@@
 ```{r}
+# Read in the data 
 tbdata <- read.csv("clean-survey-2.csv")
+# Create shortened data set  
 tbdatashort <- tbdata %>% 
@@
         col.names = c("Age Group", "Race", "Household Income", "Presidential choice")
-        ) %>% 
-  kable_styling(font_size = 5)
+        ) 
 Table1
@@
 
+In Figure [] below, we will examine the variable 'household_income' and we can see that our data is largely skewed towards households with income less than $50,000:
 ```{r}
@@
 ```
+Clearly, those with income less than $50,000 are overrepresented in the dataset as they take up 50% of the responses, therefore it is appropriate to use post stratification on our dataset.
 
+We can see a similar skewed distribution with variable 'race' in Figure [] below:
 ```{r}
@@
 ```
+It is obvious that the respondents of our survey are primarily white and there is very little representation of minorities.
 
+Lastly, by examining the variable age in Figure [] below, we can see how very little the population 76+ is represented in our dataset. 
 ```{r}
@@
 ```
+The fact that those age 76+ make up only 3% of the data could be a product of the fact that the survey was completed online.
+Clearly, the survey doesn't accurately represent those aged older than 76/ This poses the question — does our data represent the United States?
+By looking at the figure above, the answer is no.
+To adjust for the fact that the population aged 76+, we will use post stratification.
 
@@
 Another key feature is the fact that the data was collected over a short period of time— from June 25th, 2020 to July 1st, 2020.
-This significantly reduces the negative time based effects that may have affected the data ensuring that all respondents are responding on a similar ground and no one's opinion dramatically differed due to the survey taking place over a large period of time.
+This significantly reduces the negative time-based effects that may have affected the data ensuring that all respondents are responding on a similar ground and no one's opinion dramatically differed due to the survey taking place over a large period of time.
 
@@
 At the same time, this can also be viewed as a weakness because certain age groups of the United States may not be tech-savvy enough to complete an online survey.
-The older population of the united states (e.g.
+The older population of the United States (e.g.
 75+) may not be able to complete the survey because it is online which means that our data may not accurately reflect the older populations views regarding the 2020 election.
@@
 Because the sampling method is based on convenience, we may be unlucky when sampling and get a sample group that inaccurately represents the population of the US making our results meaningless.
+A potential solution to this is to use a random sampling-based method to reduce bias as much as possible.
 
@@
 Between July and November (the month of the election), many voters may not have an informed vote and their opinions may still be swayed after watching crucial debates and hearing what the leaders have to say; our data doesn’t take into consideration the people whose votes may change in the most crucial months of the election.
-A solution to this weakness can be to analyze data that may have occurred closer to the actual election so that the participants have an informed vote.
+A solution to this weakness can be to analyze data that may have occurred closer to the actual election (e.g.
+September or October) so that the participants have an informed vote.
 
@@
         digits = 6
-        ) %>% 
-  kable_styling(font_size = 5)
+        ) 
 Table6

### 2020-11-03 outputs/paper/paper.Rmd
Added Weaknesses

@@
 
-### 1: Nested Bayesian Model
+In conclusion, the findings of this paper suggest that the Biden will win the popular vote and that this is largely due to his appeal among lower income individuals and how he has note ostracized the non-white voter base.
+This is despite that fact that he is less popular among older individuals who are more likely to vote.
 
-### 2: Pre-analysis
+It also suggests that there are important demographic differences between voters that fall along race, class, and age lines.
+Distinctions that would be important to pick apart in further in depth studies where the reasons for these differences could be further understood now that they have been identified.
+
+However, as always, this analysis could be improved.
+Looking at popular vote is not the most accurate measure of presidential election in the U.S.
+One simply has to look to Hilary Clintons loss in 2016 Despite having won the popular vote 48% to Trump’s 45.9% (NY Times 2016).
+The elections in the United states are decided by the electoral college.
+
+This is a system that assigns each state a certain number of electoral votes 2 for each state and then an additional number of votes based on the population of the state (NCSL 2020).
+But what does that mean?
+That the proportion of votes ends up skewed towards smaller states.
+For example California the most populace state has a population of 39.51 million and 55 electoral college votes.
+Whereas Wyoming has a population of 578.7 thousand and 3 electoral college votes (NCSL 2020).
+This means that 1 electoral college vote in California represents 718.4 thousand Californians.
+While 1 electoral college vote in Wyoming represents 192.9 thousand Wyomingites.
+
+Furthermore, how each state casts their votes also differ some cast the totality of their ballots based upon the popular vote in their state.
+While others cast ballots based upon how many congressional districts each candidate can win in a first past the post election.
+
+What this means is that for the best forecasting accuracy it would be integral to have a more regional model that can track how electoral college votes would be cast in each state.
+Based upon each state’s electoral college system.
+
+Another area of improvement is that the independent variables for this study were selected based upon researcher assumption as to what demographic variables would be likely to influence the election.
+This introduces a lot of bias to the analysis process and could be improved.
+
+Future studies could take a pre-analysis step where a brief Anova is run across all the possible independent variables included in the Nation Scape Data Set.
+That way if there are less obvious variables that have more significant predictive effects they could be found and included in the analysis.
+Or if there are variables that would go against the researchers biases they would be easier to identify.
+
+This helps to remove the researcher from the selection process so that the data is able to speak for itself.
+
+Having a collection of follow up studies that could dig deep into; the lower significance higher income plays in political decision making, what factors are leading the extremely significant and strong racial effects of this election, and why there is an uptick in Biden support with in the age range of 56-75 could yield interesting results.
+Furthermore, having an overarching study that used pre-analysis, a Nested Bayes model, and adjusted for the effects of the electoral college could identify further voter groups of interest.
 

### 2020-11-03 outputs/paper/paper.Rmd
result

--- 2020-11-03 outputs/paper/paper.Rmd
@@
 
+The logistic regression with levels allows us to compare levels for each variable at a comparable level.
+The estimates for $\beta_{age}$ compare other groups to age from 18 to 35; the estimates for $\beta_{race}$ compares different levels to American Indian or Alaska native, and the estimates for $\beta_{income}$ compare other income levels to income level from 100k to 125k.
+For optimal display purposes, we do not state the estimated logistic regression formula.
+You can interpret this as subbing each$\beta$ in \@ref(eq:logistic).
+
+Using $\alpha = 0.05, H_0: \hat{\beta} = 0, \hat{\beta} \neq0$, we can determine if a certain variable (or its levels) have statistically significant influence towards the response variable.
+The p-value indicates the probability of having a more or equally extreme observation than the observed one, given that the null hypothesis is true.
+Naturally, a smaller p-value makes our estimate more statistically significant.
+We define “small” by setting $\alpha = 0.05$.
+A variable is said to be significantly influential to the response variable if it has a p-value smaller than 0.05.
+Therefore we can reject $H_0$ and $\beta_1 \neq 0$.
+Recall that we are finding out whether a respondent would vote for Trump in the presidential election.
+
+Observing table 1, the p-value indicates weak evidence that being white is related to one’s voting intentions(0.68 > 0.05).
+Having a family income of greater than 150k a year influences whether the respondent shall vote for Trump, but not as much compared to the other variables.
+The following levels have p-value very close to 0:
+Age > 76;
+Being Asian or Pacific Islander;
+Being NEC;
+Having a family income smaller than 25k;
+Having a family income between 25k and 50k;
+Having a family income between 75k and 100k.
+This means that these variables have a statistically significant relationship with whether the respondent shall vote for Trump.
+
+Among these variables, we notice an obvious pattern among racial groups, where respondents from a minor race are much less likely to vote for Trump.
+This makes sense because of the history behind the Republican party and the `xenophobic` image Trump makes.
+Specifically, he made many discriminatory comments against the minorities, and his travel bans from third world countries emphasize this image once again.
+
+Younger respondents(18 to 35) are less likely to vote for Trump than all age groups, while the oldest age group(more aged than 76) goes furthest in intending to vote for Trump.
+This is reasonable since older people who can potentially be more patriotic in a traditional way might harmonize Trump’s political opinions better than the young.
+The ban of TikTok certainly does not make his more likable among youth either.
+
+Respondents with less income have less incentive to vote for Trump, while this incentive roughly increases across increased income levels.
+As a capitalist himself, it is not surprising that Trump does not gain generous support among groups more towards the working class.
+
 # Discussion
@@
   predict(newdata = post_strat_cellcount_2, allow.new.level = TRUE, type="response")
-```
-
-```{r}
-post_strat_cellcount_2 %>%
-  mutate(president_predict_prop = estimate*prop) %>%
-  group_by(education_grouped) %>%
-  summarise(president_predict = sum(president_predict_prop)) %>% 
-  as.data.frame() %>% 
-  knitr::kable()
 ```

### 2020-11-03 outputs/paper/paper.Rmd
11.1

--- 2020-11-03 outputs/paper/paper.Rmd
@@
 library(lme4)
-library(merTools)
+# library(merTools)
 library(readr)
@@
 
-The first few rows of the cleaned dataset can be viewed below:
-```{r}
+The first few rows of the cleaned dataset can be viewed in Table 1 below:
+### Table 1 
+```{r, tidy =FALSE, echo =FALSE, warning= FALSE}
 # Read in the data 
@@
 
-In Figure [] below, we will examine the variable 'household_income' and we can see that our data is largely skewed towards households with income less than $50,000:
-```{r}
+In Figure 1 below, we will examine the variable 'household_income' and we can see that our data is largely skewed towards households with income less than $50,000:
+### Figure 1 
+```{r, tidy =FALSE, echo =FALSE, warning= FALSE}
 # Setup data for the pie chart and mutate a variable that details proportions for various responses. 
@@
 
-We can see a similar skewed distribution with variable 'race' in Figure [] below:
-```{r}
+We can see a similar skewed distribution with variable 'race' in Figure 2 below:
+### Figure 2
+```{r, tidy =FALSE, echo =FALSE, warning= FALSE}
 # Setup data for the pie chart and mutate a variable that details proportions for various responses. 
@@
 
-Lastly, by examining the variable age in Figure [] below, we can see how very little the population 76+ is represented in our dataset. 
-```{r}
+Lastly, by examining the variable age in Figure 3 below, we can see how very little the population 76+ is represented in our dataset. 
+### Figure 3
+```{r, tidy =FALSE, echo =FALSE, warning= FALSE}
 # Setup data for the pie chart and mutate a variable that details proportions for various responses. 
@@
 
-```{r, fig.cap='95% Prediction Intervals for forcasting the Chances that Donald Trump wins the election'}
+### Table 2 
+```{r, fig.cap='95% Prediction Intervals for forcasting the Chances that Donald Trump wins the election', tidytidy =FALSE, echo =FALSE, warning= FALSE}
 PI <- predictInterval(merMod = mod, newdata = post_strat_cellcount_2,                         
@@
 On average older individuals have higher incomes so it could be that the data is skewing younger and that is what is causing this.
-## Figure 1
-```{r}
+## Figure 4
+```{r, tidy =FALSE, echo =FALSE, warning= FALSE}
 incomegraph
@@
 
-## Figure 4
-```{r}
+## Figure 5
+```{r, tidy =FALSE, echo =FALSE, warning= FALSE}
 acs <- read_dta("post_strat_data-2.dta")
@@
 
-## Figure 2
-```{r}
+## Figure 6
+```{r, tidy =FALSE, echo =FALSE, warning= FALSE}
 agegraph
@@
 
-## Figure 5
-```{r}
+## Figure 7
+```{r, tidy =FALSE, echo =FALSE, warning= FALSE}
 ageinfoacs <- acs %>% group_by(age_group) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
@@
 
-## Figure 3
-```{r}
+## Figure 8
+```{r, tidy =FALSE, echo =FALSE, warning= FALSE}
 racegraph
@@
 
-## Figure 6
-```{r}
+## Figure 9
+```{r, tidy =FALSE, echo =FALSE, warning= FALSE}
 raceinfoacs <- acs %>% group_by(race_ethnicity) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
@@
 
-## Table 6
-```{r}
+## Table 3
+```{r, tidy =FALSE, echo =FALSE, warning= FALSE}
 Table6 <- post_strat_cellcount_2 %>% 
@@
 
+## Git Repository
+
+The link to the Git Repository is:
+
+## Code
+
+Below you will also find the R code used in this analysis:
+
+### Preamble- Setting Up Libraries and Clean Data
+
+```{r, echo=TRUE, results = "hide", warning= FALSE}
+knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
+library(tidyverse)
+library(dplyr)
+library(lme4)
+library(merTools)
+library(readr)
+library(knitr)
+library(haven)
+```
+
+```{r, echo=TRUE, results = "hide", warning= FALSE}
+clean_survey_2 <- read_csv("clean-survey-2.csv")
+mod <- glmer(binary ~ age_group + (1|education_grouped) + race_ethnicity + household_income_grouped,
+           data = clean_survey_2,
+           family = binomial()
+           )
+```
+
+```{r, echo=TRUE, results = "hide", warning= FALSE}
+# Read in the csv file for post stratification
+post_strat_cellcount_2 <- read_csv("post_strat_cellcount-2.csv")
+# get post stratification estimates using predict()
+post_strat_cellcount_2$estimate <-
+  mod %>%
+  predict(newdata = post_strat_cellcount_2, allow.new.level = TRUE, type="response")
+```
+
+```{r, echo=TRUE, results = "hide", warning= FALSE}
+aggregate(tbdata[8], list(tbdata$race_ethnicity), mean)
+
+```
+
+### Code for tables and figures used in analysis
+
+### Table 1 
+```{r, echo=TRUE, results = "hide", warning= FALSE}
+# Read in the data 
+tbdata <- read.csv("clean-survey-2.csv")
+# Create shortened data set  
+tbdatashort <- tbdata %>% 
+  dplyr::select(
+    age_group, race_ethnicity, household_income_grouped, trump_biden
+  )
+Table1 <- tbdatashort %>% 
+  head() %>% 
+  kable(align = "c",
+        format = "simple",
+        col.names = c("Age Group", "Race", "Household Income", "Presidential choice")
+        ) 
+Table1
+```
+
+### Figure 1 
+```{r, echo=TRUE, results = "hide", warning= FALSE}
+# Setup data for the pie chart and mutate a variable that details proportions for various responses. 
+incomeinfo <- tbdata %>% group_by(household_income_grouped) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
+# Graph the pie chart using ggplot; Set colour scheme, font, etc. 
+incomegraph <- incomeinfo %>% ggplot(aes(x = "", y = prop, fill = household_income_grouped)) + 
+      geom_bar(width = 1, stat = "identity") + 
+      coord_polar("y", start = 0) +
+      scale_fill_brewer(palette = "Accent") +
+      theme_void() +
+      ylab("") + xlab("") + 
+     labs(title = "Survey Distribution of Household Income", fill="Household Income") +
+     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=45, size = 4.7) +
+     theme(text = element_text(size=15))
+incomegraph
+```
+
+### Figure 2
+```{r, echo=TRUE, results = "hide", warning= FALSE}
+# Setup data for the pie chart and mutate a variable that details proportions for various responses. 
+raceinfo <- tbdata %>% group_by(race_ethnicity) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
+# Graph the pie chart using ggplot; Set colour scheme, font, etc. 
+racegraph <- raceinfo %>% ggplot(aes(x = "", y = prop, fill = race_ethnicity)) + 
+      geom_bar(width = 1, stat = "identity") + 
+      coord_polar("y", start = 0) +
+      scale_fill_brewer(palette = "Set3") +
+      theme_void() +
+      ylab("") + xlab("") + 
+     labs(title = "Survey Distribution of Respondent Race", fill="What is your race?") +
+     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=45, size = 4) +
+     theme(text = element_text(size=13))
+racegraph
+```
+
+### Figure 3
+```{r, echo=TRUE, results = "hide", warning= FALSE}
+# Setup data for the pie chart and mutate a variable that details proportions for various responses. 
+ageinfo <- tbdata %>% group_by(age_group) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
+# Graph the pie chart using ggplot; Set colour scheme, font, etc. 
+agegraph <- ageinfo %>% ggplot(aes(x = "", y = prop, fill = age_group)) + 
+      geom_bar(width = 1, stat = "identity") + 
+      coord_polar("y", start = 0) +
+      scale_fill_brewer(palette = "Set3") +
+      theme_void() +
+      ylab("") + xlab("") + 
+     labs(title = "Survey Distribution of Respondent Age", fill="Age Groups") +
+     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=45, size = 4)+
+     theme(text = element_text(size=13))
+agegraph
+```
+
+### Table 2 
+```{r, echo=TRUE, results = "hide", warning= FALSE}
+PI <- predictInterval(merMod = mod, newdata = post_strat_cellcount_2,                         
+                      level = 0.95, n.sims = 1000,                         
+                      stat = "median", type= "probability",                      
+                      include.resid.var = TRUE)
+
+ggplot(aes(x=1:30, y=fit, ymin=lwr, ymax=upr), data=PI[1:30,]) +   
+  geom_point() +   geom_linerange() +   
+  labs(x="Index", y="Prediction w/ 95% PI") + 
+  theme_bw()
+```
+
+## Figure 4
+```{r, echo=TRUE, results = "hide", warning= FALSE}
+incomegraph
+```
+
+## Figure 5
+```{r, echo=TRUE, results = "hide", warning= FALSE}
+acs <- read_dta("post_strat_data-2.dta")
+acs <- labelled::to_factor(acs)
+incomeinfoacs <- acs %>% group_by(household_income_grouped) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
+incomegraphacs <- incomeinfoacs %>% ggplot(aes(x = "", y = prop, fill = household_income_grouped)) + 
+      geom_bar(width = 1, stat = "identity") + 
+      coord_polar("y", start = 0) +
+      scale_fill_brewer(palette = "Accent") +
+      theme_void() +
+      ylab("") + xlab("") + 
+     labs(title = "ACS Distribution of Household Income", fill="Household Income") +
+     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=45, size = 4.7) +
+     theme(text = element_text(size=15))
+
+incomegraphacs
+```
+
+## Figure 6
+```{r, echo=TRUE, results = "hide", warning= FALSE}
+agegraph
+```
+
+## Figure 7
+```{r, echo=TRUE, results = "hide", warning= FALSE}
+ageinfoacs <- acs %>% group_by(age_group) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
+agegraphacs <- ageinfoacs %>% ggplot(aes(x = "", y = prop, fill = age_group)) + 
+      geom_bar(width = 1, stat = "identity") + 
+      coord_polar("y", start = 0) +
+      scale_fill_brewer(palette = "Accent") +
+      theme_void() +
+      ylab("") + xlab("") + 
+     labs(title = "ACS Distribution of Respondent Age", fill="Household Income") +
+     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=45, size = 4.7) +
+     theme(text = element_text(size=15))
+
+agegraphacs
+```
+
+## Figure 8
+```{r, echo=TRUE, results = "hide", warning= FALSE}
+racegraph
+```
+
+## Figure 9
+```{r, echo=TRUE, results = "hide", warning= FALSE}
+raceinfoacs <- acs %>% group_by(race_ethnicity) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
+racegraphacs <- raceinfoacs %>% ggplot(aes(x = "", y = prop, fill = race_ethnicity)) + 
+      geom_bar(width = 1, stat = "identity") + 
+      coord_polar("y", start = 0) +
+      scale_fill_brewer(palette = "Accent") +
+      theme_void() +
+      ylab("") + xlab("") + 
+     labs(title = "ACS Distribution of Respondent Race", fill="Household Income") +
+     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=45, size = 4.7) +
+     theme(text = element_text(size=15))
+
+racegraphacs
+```
+
+## Table 3
+```{r, echo=TRUE, results = "hide", warning= FALSE}
+Table6 <- post_strat_cellcount_2 %>% 
+  dplyr::select(
+    age_group, race_ethnicity, household_income_grouped, n, prop
+  ) %>% 
+  head() %>% 
+  kable(align = "c",
+        format = "simple",
+        col.names = c("Age Group", "Race", "Household Income", "Number of Repondents", "Proportion of Responses"),
+        digits = 6
+        ) 
+Table6
+```
+
 \newpage

### 2020-11-03 outputs/paper/paper.Rmd
Added citations

--- 2020-11-03 outputs/paper/paper.Rmd
@@
 ```{r}
+# read in data
 acs <- read_dta("post_strat_data-2.dta")
+# label the data as it is a dta
 acs <- labelled::to_factor(acs)
+#create a tibble that includes counts and proportions based on groups
 incomeinfoacs <- acs %>% group_by(household_income_grouped) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
+#Graph this tibble in a pie graph
 incomegraphacs <- incomeinfoacs %>% ggplot(aes(x = "", y = prop, fill = household_income_grouped)) + 
@@
 ```{r}
+#create a tibble that includes counts and proportions based on groups
 ageinfoacs <- acs %>% group_by(age_group) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
+#Graph this tibble
 agegraphacs <- ageinfoacs %>% ggplot(aes(x = "", y = prop, fill = age_group)) + 
@@
 ```{r}
+#create a tibble that includes counts and proportions based on groups
 raceinfoacs <- acs %>% group_by(race_ethnicity) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
+#Graph this tibble in a pie graph
 racegraphacs <- raceinfoacs %>% ggplot(aes(x = "", y = prop, fill = race_ethnicity)) + 
@@
 ```{r}
+#Generate a table that displays the first couple responses from the cell count that was generated for weighting 
 Table6 <- post_strat_cellcount_2 %>% 
@@
 ```{r include=FALSE}
+#Get general percentage of people voting for Trump by Race
 aggregate(tbdata[8], list(tbdata$race_ethnicity), mean)
-
+#get overal percentage of people voting for Trump
+mean(tbdata$binary)  
 ```
@@
 # References
+- R Core Team (2020). R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna,
+  Austria. URL https://www.R-project.org/.
+- Wickham et al., (2019). Welcome to the tidyverse. Journal of Open Source Software, 4(43), 1686, https://doi.org/10.21105/joss.01686
+- Hadley Wickham, Romain François, Lionel Henry and Kirill Müller (2020). dplyr: A Grammar of Data Manipulation. R package version
+  1.0.2. https://CRAN.R-project.org/package=dplyr
+- Douglas Bates, Martin Maechler, Ben Bolker, Steve Walker (2015). Fitting Linear Mixed-Effects Models Using lme4. Journal of
+  Statistical Software, 67(1), 1-48. doi:10.18637/jss.v067.i01.
+- Jared E. Knowles and Carl Frederick (2020). merTools: Tools for Analyzing Mixed Effect Regression Models. R package version 0.5.2.
+  https://CRAN.R-project.org/package=merTools
+- Hadley Wickham, Jim Hester and Romain Francois (2018). readr: Read Rectangular Text Data. R package version 1.3.1.
+  https://CRAN.R-project.org/package=readr
+- Yihui Xie (2020). knitr: A General-Purpose Package for Dynamic Report Generation in R. R package version 1.29.
+- Yihui Xie (2015) Dynamic Documents with R and knitr. 2nd edition. Chapman and Hall/CRC. ISBN 978-1498716963
+- Yihui Xie (2014) knitr: A Comprehensive Tool for Reproducible Research in R. In Victoria Stodden, Friedrich Leisch and Roger D.
+  Peng, editors, Implementing Reproducible Computational Research. Chapman and Hall/CRC. ISBN 978-1466561595
+- Hadley Wickham and Evan Miller (2020). haven: Import and Export 'SPSS', 'Stata' and 'SAS' Files. R package version 2.3.1.
+  https://CRAN.R-project.org/package=haven
+- JJ Allaire and Yihui Xie and Jonathan McPherson and Javier Luraschi and Kevin Ushey and Aron Atkins and Hadley Wickham and Joe Cheng
+  and Winston Chang and Richard Iannone (2020). rmarkdown: Dynamic Documents for R. R package version 2.3. URL
+  https://rmarkdown.rstudio.com.
+- Yihui Xie and J.J. Allaire and Garrett Grolemund (2018). R Markdown: The Definitive Guide. Chapman and Hall/CRC. ISBN 9781138359338.
+  URL https://bookdown.org/yihui/rmarkdown.
+- Monica Alexander. (2019, September 07). Analyzing name changes after marriage using a non-representative survey. Retrieved from https://www.monicaalexander.com/posts/2019-08-07-mrp/
+- The New York Times. (n.d.). 2016 Presidential Election Results: Donald J. Trump Wins. Retrieved from https://www.nytimes.com/elections/2016/results/president
+- US Census Bureau. (2020, October 16). Population. Retrieved from https://www.census.gov/topics/population.html
+- NCSL. (2020). The Electoral College. Retrieved from https://www.ncsl.org/research/elections-and-campaigns/the-electoral-college.aspx
+- Financial Times. (2020, October 30). Biden vs Trump: US presidential election poll tracker. Retrieved from https://ig.ft.com/us-election-2020/
+- Survey Systems (2020).
+“Sample Size Calculator.” Sample Size Calculator - Confidence Level, Confidence Interval, Sample Size, Population Size, Relevant Population - Creative Research Systems, 2020, www.surveysystem.com/sscalc.htm.
+- Amy Sorkin, John Cassidy, & Jonathan Blitzer.
+(2018).
+Donald Trump Compounds His "Shithole Countries" Bigotry with Lies.
+Retrieved from https://www.newyorker.com/news/daily-comment/donald-trump-compounds-his-shithole-countries-bigotry-with-lies
+- Philip Bump.
+(2020, September 30).
+Analysis | Donald Trump doesn't really care about the white supremacist threat, and you're not going to make him.
+Retrieved from https://www.washingtonpost.com/politics/2020/09/30/donald-trump-doesnt-really-care-about-white-supremacy-youre-not-going-make-him/
+- Kevin Liptak, & Kristen Holmes.
+(2020, July 01).
+Trump calls Black Lives Matter a 'symbol of hate' as he digs in on race.
+Retrieved from https://www.cnn.com/2020/07/01/politics/donald-trump-black-lives-matter-confederate-race/index.html

### 2020-11-03 outputs/paper/paper1.Rmd

--- 2020-11-03 outputs/paper/paper.Rmd
@@
 After our analysis, we concluded that Joe Biden will win the overall popular vote of the 2020 American presidential election.
+
+# Keywords
+- Forecasting
+- US 2020 Election
+- Multi-level Regression with Post-Stratification
+- Trump
+- Biden
 
@@
 
-The logistic regression with levels allows us to compare levels for each variable at a comparable level.
-The estimates for $\beta_{age}$ compare other groups to age from 18 to 35; the estimates for $\beta_{race}$ compares different levels to American Indian or Alaska native, and the estimates for $\beta_{income}$ compare other income levels to income level from 100k to 125k.
-For optimal display purposes, we do not state the estimated logistic regression formula.
-You can interpret this as subbing each$\beta$ in \@ref(eq:logistic).
-
-Using $\alpha = 0.05, H_0: \hat{\beta} = 0, \hat{\beta} \neq0$, we can determine if a certain variable (or its levels) have statistically significant influence towards the response variable.
-The p-value indicates the probability of having a more or equally extreme observation than the observed one, given that the null hypothesis is true.
-Naturally, a smaller p-value makes our estimate more statistically significant.
-We define “small” by setting $\alpha = 0.05$.
-A variable is said to be significantly influential to the response variable if it has a p-value smaller than 0.05.
-Therefore we can reject $H_0$ and $\beta_1 \neq 0$.
-Recall that we are finding out whether a respondent would vote for Trump in the presidential election.
-
-Observing table 1, the p-value indicates weak evidence that being white is related to one’s voting intentions(0.68 > 0.05).
-Having a family income of greater than 150k a year influences whether the respondent shall vote for Trump, but not as much compared to the other variables.
-The following levels have p-value very close to 0:
-Age > 76;
-Being Asian or Pacific Islander;
-Being NEC;
-Having a family income smaller than 25k;
-Having a family income between 25k and 50k;
-Having a family income between 75k and 100k.
-This means that these variables have a statistically significant relationship with whether the respondent shall vote for Trump.
-
-Among these variables, we notice an obvious pattern among racial groups, where respondents from a minor race are much less likely to vote for Trump.
-This makes sense because of the history behind the Republican party and the `xenophobic` image Trump makes.
-Specifically, he made many discriminatory comments against the minorities, and his travel bans from third world countries emphasize this image once again.
-
-Younger respondents(18 to 35) are less likely to vote for Trump than all age groups, while the oldest age group(more aged than 76) goes furthest in intending to vote for Trump.
-This is reasonable since older people who can potentially be more patriotic in a traditional way might harmonize Trump’s political opinions better than the young.
-The ban of TikTok certainly does not make his more likable among youth either.
-
-Respondents with less income have less incentive to vote for Trump, while this incentive roughly increases across increased income levels.
-As a capitalist himself, it is not surprising that Trump does not gain generous support among groups more towards the working class.
-
 # Discussion
@@
   predict(newdata = post_strat_cellcount_2, allow.new.level = TRUE, type="response")
+```
+
+```{r}
+post_strat_cellcount_2 %>%
+  mutate(president_predict_prop = estimate*prop) %>%
+  group_by(education_grouped) %>%
+  summarise(president_predict = sum(president_predict_prop)) %>% 
+  as.data.frame() %>% 
+  knitr::kable()
 ```

### 2020-11-03 outputs/paper/paper.Rmd
tittle

--- 2020-11-03 outputs/paper/paper.Rmd
@@
 ---
-title: "TBD"
-subtitle: "TBD"
+title: "Biden Forcested To Win the Election"
+subtitle: "Based on US Demographics of Age, Education, Household Income and Race"
 author: "Arjun Dhatt, Benjamin Draskovic, Yiqu Ding, Gantavya Gupta"
@@
 abstract: |
-  | First sentence. Second sentence. Third sentence. Fourth sentence. 
+  | In this report, we will be forecasting the winner of the upcoming US Presidential Elections 2020 between incumbent Donald Trump of the Republican Party and Joe Biden of the Democratic Party, by looking at different factors that affect a citizen’s voting intentions leading to Election Day.
+We cleaned the Nationscape dataset and chose the variables age, education, race, family income, geographic region, and mask-wearing decision which will form the basis of our Elections prediction.
+Then we used an MRP model (a combination of multilevel logistic regression and post-stratification) to analyse the factors and it also helps us in achieving a much narrower confidence interval for our prediction.
+After our analysis, we concluded that Joe Biden will win the overall popular vote of the 2020 American presidential election.
 output:
@@
 ```
-# Abstract
-
-In this report, we will be forecasting the winner of the upcoming US Presidential Elections 2020 between incumbent Donald Trump of the Republican Party and Joe Biden of the Democratic Party, by looking at different factors that affect a citizen’s voting intentions leading to Election Day.
-We cleaned the Nationscape dataset and chose the variables age, education, race, family income, geographic region, and mask-wearing decision which will form the basis of our Elections prediction.
-Then we used an MRP model (a combination of multilevel logistic regression and post-stratification) to analyse the factors and it also helps us in achieving a much narrower confidence interval for our prediction.
-After our analysis, we concluded that Joe Biden will win the overall popular vote of the 2020 American presidential election.
 

### 2020-11-03 outputs/paper/paper2.Rmd
Adding final version

--- 2020-11-03 outputs/paper/paper.Rmd
@@
 library(lme4)
-# library(merTools)
+library(merTools)
 library(readr)
@@
 
+### Table 2
 ### Summary Table
@@
 
+The logistic regression with levels allows us to compare levels for each variable at a comparable level.
+The estimates for $\beta_{age}$ compare other groups to age from 18 to 35; the estimates for $\beta_{race}$ compares different levels to American Indian or Alaska native, and the estimates for $\beta_{income}$ compare other income levels to income level from 100k to 125k.
+For optimal display purposes, we do not state the estimated logistic regression formula.
+You can interpret this as subbing each$\beta$ in \@ref(eq:logistic).
+
+Using $\alpha = 0.05, H_0: \hat{\beta} = 0, \hat{\beta} \neq0$, we can determine if a certain variable (or its levels) have statistically significant influence towards the response variable.
+The p-value indicates the probability of having a more or equally extreme observation than the observed one, given that the null hypothesis is true.
+Naturally, a smaller p-value makes our estimate more statistically significant.
+We define “small” by setting $\alpha = 0.05$.
+A variable is said to be significantly influential to the response variable if it has a p-value smaller than 0.05.
+Therefore we can reject $H_0$ and $\beta_1 \neq 0$.
+Recall that we are finding out whether a respondent would vote for Trump in the presidential election.
+
+Observing table 1, the p-value indicates weak evidence that being white is related to one’s voting intentions(0.68 > 0.05).
+Having a family income of greater than 150k a year influences whether the respondent shall vote for Trump, but not as much compared to the other variables.
+The following levels have p-value very close to 0:
+Age > 76;
+Being Asian or Pacific Islander;
+Being NEC;
+Having a family income smaller than 25k;
+Having a family income between 25k and 50k;
+Having a family income between 75k and 100k.
+This means that these variables have a statistically significant relationship with whether the respondent shall vote for Trump.
+
+Among these variables, we notice an obvious pattern among racial groups, where respondents from a minor race are much less likely to vote for Trump.
+This makes sense because of the history behind the Republican party and the `xenophobic` image Trump makes.
+Specifically, he made many discriminatory comments against the minorities, and his travel bans from third world countries emphasize this image once again.
+
+Younger respondents(18 to 35) are less likely to vote for Trump than all age groups, while the oldest age group(more aged than 76) goes furthest in intending to vote for Trump.
+This is reasonable since older people who can potentially be more patriotic in a traditional way might harmonize Trump’s political opinions better than the young.
+The ban of TikTok certainly does not make his more likable among youth either.
+
+Respondents with less income have less incentive to vote for Trump, while this incentive roughly increases across increased income levels.
+As a capitalist himself, it is not surprising that Trump does not gain generous support among groups more towards the working class.
+
 # Discussion
-
-```{r}
-# Read in the csv file for post stratification
-post_strat_cellcount_2 <- read_csv("post_strat_cellcount-2.csv")
-# get post stratification estimates using predict()
-post_strat_cellcount_2$estimate <-
-  mod %>%
-  predict(newdata = post_strat_cellcount_2, allow.new.level = TRUE, type="response")
-```
-
-```{r}
-post_strat_cellcount_2 %>%
-  mutate(president_predict_prop = estimate*prop) %>%
-  group_by(education_grouped) %>%
-  summarise(president_predict = sum(president_predict_prop)) %>% 
-  as.data.frame() %>% 
-  knitr::kable()
-```
-
-### Table 2 
-```{r, fig.cap='95% Prediction Intervals for forcasting the Chances that Donald Trump wins the election', tidytidy =FALSE, echo =FALSE, warning= FALSE}
-PI <- predictInterval(merMod = mod, newdata = post_strat_cellcount_2,                         
-                      level = 0.95, n.sims = 1000,                         
-                      stat = "median", type= "probability",                      
-                      include.resid.var = TRUE)
-
-ggplot(aes(x=1:30, y=fit, ymin=lwr, ymax=upr), data=PI[1:30,]) +   
-  geom_point() +   geom_linerange() +   
-  labs(x="Index", y="Prediction w/ 95% PI") + 
-  theme_bw()
-```
 
@@
 On average older individuals have higher incomes so it could be that the data is skewing younger and that is what is causing this.
-## Figure 4
+### Figure 1
 ```{r, tidy =FALSE, echo =FALSE, warning= FALSE}
@@
 
-## Figure 5
-```{r, tidy =FALSE, echo =FALSE, warning= FALSE}
+### Figure 4
+```{r}
+# read in data
 acs <- read_dta("post_strat_data-2.dta")
+# label the data as it is a dta
 acs <- labelled::to_factor(acs)
+#create a tibble that includes counts and proportions based on groups
 incomeinfoacs <- acs %>% group_by(household_income_grouped) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
+#Graph this tibble in a pie graph
 incomegraphacs <- incomeinfoacs %>% ggplot(aes(x = "", y = prop, fill = household_income_grouped)) + 
@@
 
-## Figure 6
+### Figure 3
 ```{r, tidy =FALSE, echo =FALSE, warning= FALSE}
@@
 
-## Figure 7
-```{r, tidy =FALSE, echo =FALSE, warning= FALSE}
+### Figure 5
+```{r}
+#create a tibble that includes counts and proportions based on groups
 ageinfoacs <- acs %>% group_by(age_group) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
+#Graph this tibble
 agegraphacs <- ageinfoacs %>% ggplot(aes(x = "", y = prop, fill = age_group)) + 
@@
 
-## Figure 8
+### Figure 2
 ```{r, tidy =FALSE, echo =FALSE, warning= FALSE}
@@
 
-## Figure 9
+### Figure 6
 ```{r, tidy =FALSE, echo =FALSE, warning= FALSE}
+#create a tibble that includes counts and proportions based on groups
 raceinfoacs <- acs %>% group_by(race_ethnicity) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
+#Graph this tibble in a pie graph
 racegraphacs <- raceinfoacs %>% ggplot(aes(x = "", y = prop, fill = race_ethnicity)) + 
@@
 ```{r, tidy =FALSE, echo =FALSE, warning= FALSE}
+# Read in the csv file for post stratification
+post_strat_cellcount_2 <- read_csv("post_strat_cellcount-2.csv")
+#Generate a table that displays the first couple responses from the cell count that was generated for weighting 
 Table6 <- post_strat_cellcount_2 %>% 
@@
 
-### Table 2 
+```{r echo=TRUE, results = "hide", warning= FALSE}
+# Read in the csv file for post stratification
+post_strat_cellcount_2 <- read_csv("post_strat_cellcount-2.csv")
+# get post stratification estimates using predict()
+post_strat_cellcount_2$estimate <-
+  mod %>%
+  predict(newdata = post_strat_cellcount_2, allow.new.level = TRUE, type="response")
+```
+
+# Weighting code that did not run 
+```{r echo=TRUE, results = "hide", warning= FALSE}
+post_strat_cellcount_2 %>%
+  mutate(president_predict_prop = estimate*prop) %>%
+  group_by(education_grouped) %>%
+  summarise(president_predict = sum(president_predict_prop)) %>% 
+  as.data.frame() %>% 
+  knitr::kable()
+```
+
 ```{r, echo=TRUE, results = "hide", warning= FALSE}
@@
 ```
-
 ## Figure 4
@@
 # References
+- R Core Team (2020). R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna,
+  Austria. URL https://www.R-project.org/.
+- Wickham et al., (2019). Welcome to the tidyverse. Journal of Open Source Software, 4(43), 1686, https://doi.org/10.21105/joss.01686
+- Hadley Wickham, Romain François, Lionel Henry and Kirill Müller (2020). dplyr: A Grammar of Data Manipulation. R package version
+  1.0.2. https://CRAN.R-project.org/package=dplyr
+- Douglas Bates, Martin Maechler, Ben Bolker, Steve Walker (2015). Fitting Linear Mixed-Effects Models Using lme4. Journal of
+  Statistical Software, 67(1), 1-48. doi:10.18637/jss.v067.i01.
+- Jared E. Knowles and Carl Frederick (2020). merTools: Tools for Analyzing Mixed Effect Regression Models. R package version 0.5.2.
+  https://CRAN.R-project.org/package=merTools
+- Hadley Wickham, Jim Hester and Romain Francois (2018). readr: Read Rectangular Text Data. R package version 1.3.1.
+  https://CRAN.R-project.org/package=readr
+- Yihui Xie (2020). knitr: A General-Purpose Package for Dynamic Report Generation in R. R package version 1.29.
+- Yihui Xie (2015) Dynamic Documents with R and knitr. 2nd edition. Chapman and Hall/CRC. ISBN 978-1498716963
+- Yihui Xie (2014) knitr: A Comprehensive Tool for Reproducible Research in R. In Victoria Stodden, Friedrich Leisch and Roger D.
+  Peng, editors, Implementing Reproducible Computational Research. Chapman and Hall/CRC. ISBN 978-1466561595
+- Hadley Wickham and Evan Miller (2020). haven: Import and Export 'SPSS', 'Stata' and 'SAS' Files. R package version 2.3.1.
+  https://CRAN.R-project.org/package=haven
+- JJ Allaire and Yihui Xie and Jonathan McPherson and Javier Luraschi and Kevin Ushey and Aron Atkins and Hadley Wickham and Joe Cheng
+  and Winston Chang and Richard Iannone (2020). rmarkdown: Dynamic Documents for R. R package version 2.3. URL
+  https://rmarkdown.rstudio.com.
+- Yihui Xie and J.J. Allaire and Garrett Grolemund (2018). R Markdown: The Definitive Guide. Chapman and Hall/CRC. ISBN 9781138359338.
+  URL https://bookdown.org/yihui/rmarkdown.
+- Monica Alexander. (2019, September 07). Analyzing name changes after marriage using a non-representative survey. Retrieved from https://www.monicaalexander.com/posts/2019-08-07-mrp/
+- The New York Times. (n.d.). 2016 Presidential Election Results: Donald J. Trump Wins. Retrieved from https://www.nytimes.com/elections/2016/results/president
+- US Census Bureau. (2020, October 16). Population. Retrieved from https://www.census.gov/topics/population.html
+- NCSL. (2020). The Electoral College. Retrieved from https://www.ncsl.org/research/elections-and-campaigns/the-electoral-college.aspx
+- Financial Times. (2020, October 30). Biden vs Trump: US presidential election poll tracker. Retrieved from https://ig.ft.com/us-election-2020/
+- Survey Systems (2020).
+“Sample Size Calculator.” Sample Size Calculator - Confidence Level, Confidence Interval, Sample Size, Population Size, Relevant Population - Creative Research Systems, 2020, www.surveysystem.com/sscalc.htm.
+- Amy Sorkin, John Cassidy, & Jonathan Blitzer.
+(2018).
+Donald Trump Compounds His "Shithole Countries" Bigotry with Lies.
+Retrieved from https://www.newyorker.com/news/daily-comment/donald-trump-compounds-his-shithole-countries-bigotry-with-lies
+- Philip Bump.
+(2020, September 30).
+Analysis | Donald Trump doesn't really care about the white supremacist threat, and you're not going to make him.
+Retrieved from https://www.washingtonpost.com/politics/2020/09/30/donald-trump-doesnt-really-care-about-white-supremacy-youre-not-going-make-him/
+- Kevin Liptak, & Kristen Holmes.
+(2020, July 01).
+Trump calls Black Lives Matter a 'symbol of hate' as he digs in on race.
+Retrieved from https://www.cnn.com/2020/07/01/politics/donald-trump-black-lives-matter-confederate-race/index.html
+- Democracy Fund, & UCLA. (2020). Nation Scape Data Set. Retrieved from https://www.voterstudygroup.org/publication/nationscape-data-set
+- US Census Bureau. (2018). American Community Survey 2018. Retrieved from https://usa.ipums.org/usa/index.shtml

### 2020-11-03 outputs/paper/paper2.Rmd
Repo Cleaning

@@
 The first few rows of the cleaned dataset can be viewed in Table 1 below:
+
 ### Table 1 
@@
 In Figure 1 below, we will examine the variable 'household_income' and we can see that our data is largely skewed towards households with income less than $50,000:
+
 ### Figure 1 
@@
 We can see a similar skewed distribution with variable 'race' in Figure 2 below:
+
 ### Figure 2
@@
 Lastly, by examining the variable age in Figure 3 below, we can see how very little the population 76+ is represented in our dataset.
+
 ### Figure 3
@@
 ```
+
 The fact that those age 76+ make up only 3% of the data could be a product of the fact that the survey was completed online.
@@
 ### Table 2
+
 ### Summary Table
@@
 On average older individuals have higher incomes so it could be that the data is skewing younger and that is what is causing this.
+
 ### Figure 1

### 2020-11-03 scripts/01-data-cleaning-survey.R
More Cleaning

@@ -1,180 +1,0 @@
-#### Preamble ####
-# Purpose: The purpose of this code is to prepare and clean the Nationscape Data Set downloaded from the Democracy Fund 
-# Voter Study Group. Because we aren't looking at each and every one of the more than 200 variables included in the dataset,
-# we want to clean the dataset so that it only includes variables that we are interested in. To address this issue, we only
-# included the variables that we are interested in. Also, in our analysis, we will only be looking at who is going to win 
-# the popular vote between Donald Trump and Joe Biden, therefore we cleaned the results so that they only showcase those 
-# willing to vote for Donald Trump or Joe Biden. We also added another variable that was not originally included in the
-# dataset to make vote a binary variable. To adress issues with some variables containing an excessive amount of options 
-# (e.g. age, education etc.) we created additional variables that would group the values of the variable so that they are 
-# easier to analyze A problem we encountered with the raw dataset was that a lot of the values were shown as N/A; to address
-# this issue, we also cleaned the dataset so that it removed all N/A values meaning for each row in the dataset, every column 
-# has a meaningful value.
-# Author: Arjun Dhatt, Ben Draskovic, Gantavya Gupta, Yiqu Ding 
-# Data: 2 November 2020
-# Contact: arjun.dhatt@mail.utoronto.ca 
-# License: MIT
-# Pre-requisites: 
-## 1. Go to: https://www.voterstudygroup.org/publication/nationscape-data-set
-## 2. Look for the 'Download the Full Data Set' heading and enter your information and submit your request. 
-## After a short period of time, you will have received an email containing links to the dataset. 
-## 3. Click on the link included in the email. Under the header 'Download Resources', download the .dta. 
-## files. This will be a zip file, therefore you will have to unzip it.
-## 4. After unzipping the file, open 'phase_2_v20200814' -> 'ns20200625' -> '01-data_cleaning-survey.R'. 
-## We open the folder pertaining to 'ns20200625' because we want data from June 25th, 2020. 
[…]

### 2020-11-03 scripts/01-data_cleaning-post-strat.R

@@ -1,156 +1,0 @@
-#### Preamble ####
-# Purpose: To prepare the survey data downloaded from IPUMS USA based on the 2018 ACS survey. 
-# This data set will be used in the post-stratification process. MEaning that the data will be 
-# adjusted to match the categories used in the cleaned Nation-Scape Data set. Then bin counts will
-# be generated so that the two data sets may be compared. 
-# Author: Arjun Dhatt, Ben Draskovic, Gantavya Gupta, Yiqu Ding 
-# Data: 2 November 2020
-# Contact: ben.draskovic@mail.utoronto.ca
-# License: MIT
-# Pre-requisites: 
-# - Need to have downloaded the ACS data and saved it to inputs/ACS
-# - Set up a gitignore in order to retain the privacy of the data 
-
-
-#### Workspace setup ####
-library(haven)
-library(tidyverse)
-library(dplyr)
-# Read in the raw data. 
-raw_data <- read_dta("inputs/ACS/usa_00001.dta.gz"
-)
-# Add the labels
-raw_data <- labelled::to_factor(raw_data)
-
-# Select variables of interest for analysis
-names(raw_data)
-
-reduced_data <- 
-  raw_data %>% 
-  select(age, 
-         race, 
-         hispan,
-         educ,
-         ftotinc)
-rm(raw_data)
-
-#Remove all na values from the data (For Family income NA was 9999999)
-#Remove all children under 18
-prep_data <- reduced_data %>% 
-  filter(
-    ftotinc<9999999,
-    as.integer(age)>18,
-    !is.na(age),
-    !is.na(race),
-    !is.na(hispan),
-  )
-# This removes 799,716 respondants from the data 
-
-
-#Group the education responses into groups that best match the groups in UCLA Survey being used
-#Notably an estimate as to when a degree would be completed had to be used for this we used the estimate of 3 years or above
-recode_key_education <- c(  
-  "n/a or no schooling" = "Less than HS",
-  "nursery school to grade 4" = "Less than HS",
-  "grade 5, 6, 7, or 8" = "Less than HS",
-  "grade 9" = "Completed Some HS",
-  "grade 10" = "Completed Some HS",
-  "grade 11" = "Completed Some HS",
-  "grade 12" = "Completed HS",
-  "1 year of college" = "Participated in Higher Education",
[…]
